\documentclass{article}

\usepackage[preprint]{neurips_2026}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{fancyvrb}
\usepackage{listings}

\lstdefinestyle{kisspy}{
  language=Python,
  basicstyle=\ttfamily\scriptsize,
  keywordstyle=\color[rgb]{0.0,0.0,0.8}\bfseries,
  commentstyle=\color[rgb]{0.25,0.5,0.35}\itshape,
  stringstyle=\color[rgb]{0.73,0.13,0.13},
  showstringspaces=false,
  frame=single,
  framesep=2mm,
  numbers=left,
  numberstyle=\tiny\color{gray},
  numbersep=5pt,
  breaklines=true,
  tabsize=4,
  captionpos=b,
}
\lstdefinestyle{prompt}{
  language={},
  basicstyle=\ttfamily\scriptsize,
  frame=single,
  framesep=2mm,
  breaklines=true,
  columns=fullflexible,
}

\newcommand{\kisssys}{\textsc{KISS Sorcar}}
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\eg}{\textit{e.g.}}

\title{Software Engineering KISS Sorcar with KISS Sorcar}

\author{%
Koushik Sen \\ EECS Department, UC Berkeley\\ \texttt{ksen@berkeley.edu} \\ }

\begin{document}

\maketitle

\begin{center}
\textit{"Everything should be made as simple as possible, but not simpler." — Albert Einstein}
\end{center}

\begin{abstract}
We describe how we built \kisssys{}---a general-purpose AI assistant and
integrated development environment---using \kisssys{} itself.
Over 44~days (April~22 to June~5, 2026), the developer issued
3,099~tasks through the system's own interface.
We analyzed every task in the system's SQLite usage log
and identified seven recurring patterns: test-first bug fixing,
iterative feature construction, periodic code hygiene, paper--code
co-evolution, defensive revert, architecture investigation before
change, and multi-channel general assistance.
The developer used \kisssys{} not only to write code across
Python, TypeScript, JavaScript, CSS, and \LaTeX{}, but also to
control smart-home lights via the Govee API, plan trips,
send Slack and iMessage messages, check email, query weather
and stock prices, build a website, prepare lecture slides,
audit security reports, and refuse an unethical hacking request.
The software ecosystem touched by these tasks spans
VS~Code, Git/GitHub, \LaTeX{}/pdflatex, SQLite, Playwright/Chromium,
Cloudflare Tunnels, Docker, pytest, and a dozen third-party agent
integrations.
We find that six established software engineering principles---encoded
in a structured system prompt and a five-layer agent
hierarchy totaling roughly 3,350~lines of code---explain the patterns
and produce an AI assistant that achieves a 62.2\%
pass rate on Terminal Bench~2.0 without benchmark-specific tuning.
\end{abstract}

%----------------------------------------------------------------------
\section{Introduction}
\label{sec:intro}
%----------------------------------------------------------------------

Large language models generate code and call tools fluently.
Deploying them as practical software engineering assistants, however,
still exposes persistent gaps: finite context windows, sessions
derailed by a single mistake, agents stuck in dead ends, and
generated changes that resist review or revert~\cite{yang2024sweagent,
wang2024openhands}.

We built \kisssys{}, an AI assistant and IDE, on top of the KISS Agent
Framework~\cite{sen2026kiss}.
The name reflects the \emph{Keep It Simple, Stupid} design philosophy:
each component does one thing, each concern lives in one place,
and the overall system avoids unnecessary abstraction.
The entire framework comprises roughly 3,350~lines of core agent code
spread across five layers, each adding exactly one concern:

\begin{enumerate}[nosep]
  \item \textbf{KISS Agent}---budget-tracked ReAct loop~\cite{yao2023react}.
  \item \textbf{Relentless Agent}---automatic continuation across
        sub-sessions via summarization.
  \item \textbf{Sorcar Agent}---coding tools, browser automation,
        parallel sub-agents.
  \item \textbf{Chat Sorcar Agent}---persistent multi-turn chat.
  \item \textbf{Worktree Sorcar Agent}---git worktree isolation per task.
\end{enumerate}

The defining feature of this project is that we built it with itself.
From the second month onward, every code change, every bug fix, every
feature addition, and every paper draft was produced by \kisssys{}
operating on its own repository.
This \emph{self-hosting} discipline turns the system into a continuous
stress test: any bug the agent introduces impairs its own ability to
function, and must be fixed immediately.

To understand how this process works in practice, we analyzed all
3,099~tasks recorded in the system's SQLite usage log
(\texttt{\textasciitilde/.kiss/sorcar.db}) over 44~days of active development.
The tasks fall into seven recurring patterns
(Section~\ref{sec:patterns}), each grounded in a software engineering
principle (Section~\ref{sec:principles}).
Table~\ref{tab:categories} summarizes the task distribution.

\begin{table}[t]
\centering
\caption{Task categories identified in the 3,099-task usage log.
Counts are approximate because tasks often span categories.}
\label{tab:categories}
\begin{tabular}{lrr}
\toprule
\textbf{Category} & \textbf{Count} & \textbf{\%} \\
\midrule
Bug finding, reproducing, and fixing   & $\sim$620  & 20 \\
Feature implementation                 & $\sim$520  & 17 \\
UI/UX refinement                       & $\sim$360  & 12 \\
Paper writing and building             & $\sim$310  & 10 \\
Code quality / refactoring             & $\sim$250  &  8 \\
Testing and CI                         & $\sim$210  &  7 \\
Git operations                         & $\sim$155  &  5 \\
System prompt engineering              & $\sim$100  &  3 \\
General assistance (weather, travel,
  shopping, stocks, research)          & $\sim$210  &  7 \\
Communication (Slack, iMessage, email) & $\sim$90   &  3 \\
Smart-home control                     & $\sim$50   &  2 \\
Greetings and identity                 & $\sim$150  &  5 \\
Other (security audits, installation,
  architecture investigation)          & $\sim$150  &  5 \\
\bottomrule
\end{tabular}
\end{table}

The rest of the paper is organized as follows.
Section~\ref{sec:background} surveys related work.
Section~\ref{sec:patterns} presents the seven usage patterns with
concrete examples from the log.
Section~\ref{sec:principles} maps each pattern to a software
engineering principle.
Section~\ref{sec:software} catalogs the software ecosystem.
Section~\ref{sec:system-prompt} shows how the principles are
encoded in the system prompt.
Section~\ref{sec:evaluation} reports evaluation results.
Section~\ref{sec:discussion} discusses lessons learned.
Section~\ref{sec:conclusion} concludes.

%----------------------------------------------------------------------
\section{Background and Related Work}
\label{sec:background}
%----------------------------------------------------------------------

\subsection{AI Coding Agents}

SWE-Agent~\cite{yang2024sweagent} and OpenHands~\cite{wang2024openhands}
provide LLM-based agents for resolving GitHub issues in single sessions.
Agentless~\cite{xia2024agentless} shows that a two-phase
localize-then-repair pipeline can match agentic approaches on
SWE-bench~\cite{jimenez2024swebench}.
Industrial products---GitHub Copilot~\cite{copilot2021},
Cursor~\cite{cursor2024}, Devin~\cite{devin2024},
Claude~Code~\cite{claudecode2025}, OpenAI Codex~\cite{codex2025},
and Aider~\cite{aider2023}---offer varying degrees of autonomy.
Cursor's Composer~2~\cite{cursor2026composer2} uses large-scale
reinforcement learning on a custom fine-tuned model.
Multi-agent systems such as
ChatDev~\cite{qian2024chatdev},
MetaGPT~\cite{hong2024metagpt}, and
AutoGen~\cite{wu2023autogen} simulate organizations of specialist
roles.

Our approach differs.
Rather than training a specialized model or orchestrating many agents,
we use a single agent with a structured system prompt and a layered
architecture in which each layer solves one concern.

\subsection{Software Engineering Principles}

The principles we apply are not new.
Parnas~\cite{parnas1972criteria} established information hiding
and modular decomposition.
Dijkstra~\cite{dijkstra1968goto} argued for structured programming.
Brooks~\cite{brooks1995mythical} warned against accidental complexity.
Beck~\cite{beck2003tdd} codified test-driven development.
Hunt and Thomas~\cite{hunt1999pragmatic} distilled pragmatic
engineering heuristics.
Martin~\cite{martin2008clean} catalogued clean-code practices.

What is new is the context: applying these principles to an AI agent
that writes its own code.

\subsection{Self-Hosting in Software}

Self-hosting---a system that builds or runs itself---is a venerable
practice.
Thompson~\cite{thompson1984reflections} explored the trust
implications of self-compiling compilers.
Raymond~\cite{raymond1999cathedral} observed that eating your own
dog food exposes bugs that no amount of external testing reveals.
We apply this idea to an AI agent: \kisssys{} develops itself, and
every defect it introduces is a defect it must then live with.

%----------------------------------------------------------------------
\section{Usage Patterns}
\label{sec:patterns}
%----------------------------------------------------------------------

We examined all 3,099~tasks in the usage log and identified seven
recurring patterns.
Each pattern is a workflow that the developer repeated dozens or
hundreds of times.

\paragraph{Methodology.}
The data source is the system's own SQLite database,
\texttt{\textasciitilde/.kiss/sorcar.db}, which the Chat Sorcar Agent
(layer~4 of the hierarchy in Section~\ref{sec:intro}) populates
automatically after every task.
The schema is intentionally small: a \texttt{task\_history} table
stores one row per task (timestamp, the verbatim task description,
the result summary, a 32-character \texttt{chat\_id}, and a JSON
\texttt{extra} field of metadata such as model name, token count, and
dollar cost); an \texttt{events} table stores the full per-step
trajectory; a \texttt{frequent\_tasks} table maintains a frequency
count per distinct task string; and \texttt{model\_usage} and
\texttt{file\_usage} tables track which models and files were
touched.
Because every task the developer issued---whether a coding request, a
weather query, or a smart-home command---flows through the same Chat
Sorcar Agent, the log is a complete, unfiltered record of how the
system was actually used.
The 3,099~tasks span 44~days and group into 877~distinct chat
sessions, an average of roughly 3.5~tasks per session, confirming the
iterative, multi-turn nature of the interaction
(Section~\ref{sec:p-iterative}).
We extracted patterns by three complementary methods:
(i)~clustering tasks by the \texttt{frequent\_tasks} frequency table,
which surfaces verbatim repeated commands such as
``\texttt{uv run check -{}-full and fix}'' (50~occurrences) and
``\texttt{git push origin}'' (13~occurrences);
(ii)~full-text \texttt{LIKE} queries over the task descriptions to
count phrasings (\eg{} 73~tasks contain ``build the paper,''
105~contain ``\texttt{uv run check}''); and
(iii)~manual reading of representative tasks within each cluster to
recover the underlying workflow.
The category counts in Table~\ref{tab:categories} are approximate
because a single task often serves more than one purpose---``fix the
race condition and run the full suite'' is simultaneously a bug fix
and a testing task.
Task numbers cited below (\eg{} Task~344) refer to the
\texttt{task\_history} row identifiers, which increase monotonically
with time and therefore double as a rough chronological index.

%......................................................................
\subsection{Pattern 1: Test-First Bug Fixing}
\label{sec:p-test-first}
%......................................................................

The most common pattern (roughly 20\% of all tasks) follows a
rigid three-step protocol:

\begin{enumerate}[nosep]
  \item The developer reports a bug in natural language.
  \item The agent writes an integration test that reproduces the bug.
  \item The agent fixes the root cause and verifies the test passes.
\end{enumerate}

\noindent The canonical phrasing, which appears in hundreds of tasks, is:
\begin{quote}\small
``Can you reproduce the bug by writing an integration test?
Then fix it.''
\end{quote}

This phrasing is not a coincidence; it is the conversational echo of
an instruction baked into the system prompt itself
(Section~\ref{sec:system-prompt}): ``When fixing bugs, issues, or
race conditions: write an integration test that reproduces the
problem first, then fix the code, then verify the test passes.''
The developer internalized the agent's own protocol and began phrasing
bug reports in the form the agent handles best.
The discipline serves two purposes that the developer relied on
repeatedly.
First, a test that fails before the fix and passes after it is
\emph{evidence} that the reported bug was real and that the change
addressed it, rather than a plausible-looking edit that touches the
wrong code path.
Second, writing the test forces the agent to localize the defect
precisely---to identify the exact module, function, and input that
triggers the failure---before it is allowed to modify anything,
which curbs the model's tendency to patch symptoms.

\paragraph{Example.}
Task~1236: ``\texttt{ask\_user\_question} is not showing its window
in the web/mobile app.''
The agent was instructed to write a test first, then fix.
The bug reports in the log are strikingly specific, which is what
makes the test-first protocol tractable.
Representative verbatim examples include:
``In the last task, the merge/diff interface was not launched and
Auto-commit and merge buttons were not shown.  Reproduce the issue
\ldots then fix it'';
``In the last task, you made changes, but they were not reflected
in the actual file system.  Can you find and reproduce that\ldots'';
and ``the settings are not persisted across tasks.  Repro the issue
by writing an integration test.''
This protocol was applied to bugs as varied as missing diff/merge
UI triggers for \LaTeX{} files (Task~109), auto-committed changes
not appearing in reports (Task~104), thinking blocks leaking outside
thought panels (Task~741), and race conditions in concurrent tab
management (Task~65).

\paragraph{Concurrency bugs.}
A distinctive sub-class of test-first tasks targets race conditions
that only the self-hosting setting exposes, because the developer runs
multiple IDE tabs and a remote web server against the same repository
at once.
Examples from the log include
``Fix the persistence module's SQLite connection handling with a
read-write lock on \texttt{\_load\_chat\_context} to eliminate
concurrent-access errors,''
``Add integration tests for nested parallel execution where
sub-agents themselves invoke \texttt{run\_parallel}, to verify budget
\ldots is correct,''
and a report of errors ``when multiple tasks from local extension and
from remote web server are using'' the database simultaneously.
For these, the system prompt prescribes a specific technique the
developer invoked by name: ``To confirm race conditions: add a random
sleep (\textless0.1s) before the suspected racing statements,''
which widens the race window so the bug manifests deterministically
in a test before the lock or thread-local fix is applied.

\paragraph{Variant: defensive revert.}
When a fix introduced a regression, the developer's next task was
often ``can you get rid of the last commit to main?''
(Tasks~18, 56, 110, 209, 395, 545, 909, 920, 949, 1877, 1996).
The exact string ``get rid of the last commit'' (with minor
variations such as ``\ldots to main,'' ``\ldots from main,''
``\ldots from main and origin,'' and ``\ldots in main?'') recurs more
than 30~times in the log, making it one of the most frequent
recovery commands.
It functions as a manual rollback mechanism that complements the
Worktree Sorcar Agent's branch-per-task isolation: even though each
task runs on its own branch and the user reviews the diff before
merging, a regression can still slip through review and land on
\texttt{main}.
When that happens, the developer's reflex is to undo first and
re-attempt with a fresh approach, rather than to pile a corrective
patch on top of a broken commit---a manual application of the
defensive-programming principle discussed in
Section~\ref{sec:defensive}.

%......................................................................
\subsection{Pattern 2: Iterative Feature Construction}
\label{sec:p-iterative}
%......................................................................

Features were never built in a single task.
The developer described a feature, observed the result, then issued
follow-up tasks to refine behavior, fix edge cases, and polish
the UI.
A single feature could span 5--20~tasks.
This pattern is the dominant explanation for the 877~chat
sessions in the log: a feature is typically developed within one chat
session, and the Chat Sorcar Agent's persistence
lets each follow-up task reference the
prior tasks and results in the same session without the developer
re-stating context.
The workflow is therefore a tight loop of
\emph{describe~$\rightarrow$~observe~$\rightarrow$~refine}: the
developer issues a short natural-language request, watches the agent's
result in the IDE, and immediately issues the next task to correct
whatever fell short.
Crucially, the refinement is interleaved with Pattern~1: roughly half
the follow-up tasks in a feature session are themselves bug reports
(``the button does not appear on mobile''), so a feature session is
usually a chain of small features punctuated by test-first fixes.

\paragraph{Example: remote web server.}
The remote-access feature started with Task~344:
\begin{quote}\small
``Can you implement a new feature where the user can access KISS
Sorcar from the internet from a mobile device or any device with a
browser?''
\end{quote}
This was followed by 60+ tasks over three days: adding HTTPS/TLS
(Task~374), fixing mobile layout (Task~452), adding password
authentication (Task~878), displaying the Cloudflare tunnel URL in
the welcome page (Tasks~396--415), handling MacBook lid-close
disconnections (Task~412), and emailing the URL to the user
(Tasks~386--392).
The trajectory of this single feature is a microcosm of the whole
pattern: the first task delivered a minimal working server, and every
subsequent task hardened one concrete dimension---security (TLS, then
password auth), reach (mobile layout), discoverability (URL on the
welcome page, URL by email), and robustness (surviving a lid-close
disconnection).
None of these refinements was specified up front; each was prompted by
the developer actually using the feature on a phone and hitting its
limits.
This is iterative construction in the literal sense: the specification
emerged from use, not from a design document.

\paragraph{Example: demo mode.}
Demo mode started with Task~45 and was refined over Tasks~46, 53,
191, 219--220 across multiple days, adding streaming animation,
stop-button behavior, and cross-task continuation.
A representative refinement task reads: ``In the demo mode, I see the
welcome page when the demo switches from one task to another.  The
next task animation MUST'' begin without the intervening welcome
screen---a single-sentence bug report that triggered a targeted fix
to the demo state machine.
The multi-day span (Tasks~45 through~220) shows that a feature is not
``done'' when it first works; it is revisited whenever the developer
notices a rough edge during ordinary use.

%......................................................................
\subsection{Pattern 3: Periodic Code Hygiene}
\label{sec:p-hygiene}
%......................................................................

At regular intervals---roughly every 20--30~tasks---the developer ran
a sweep:

\begin{itemize}[nosep]
  \item ``\texttt{uv run check --full and fix}''
        (Tasks~26, 60, 72, 73, 83, 203, 212, \ldots).
        The exact string ``\texttt{uv run check -{}-full and fix}''
        is the second most frequent command in the entire log
        (50~occurrences in the \texttt{frequent\_tasks} table), and
        105~tasks in total mention ``\texttt{uv run check}.''
  \item ``Can you thoroughly find all bugs, redundancies, and
        inconsistencies in \texttt{PWD/src/kiss/agents/vscode/}?''
        (Tasks~1, 6, 15, 17, 19, 23, 153, 425--427, 716, 918, 978, 981).
  \item ``Run all tests and fix tests only if there is no bug in
        the code.  Report the bugs.''
        (Tasks~798, 840, 866, 890--891, 961, 986, 990, 1013, 1126, 1128, 1158).
        A closely related verbatim phrasing---``can you run all tests
        and report the cause of failing tests?  Do not modify any''
        code---appears 22~times.
\end{itemize}

These sweeps function as a periodic ``garbage collection'' for code
quality.
They catch drift introduced by feature work, remove dead code left
behind by refactors, and ensure the test suite stays green.
Three observations are worth drawing out.
First, the sweeps are deliberately \emph{decoupled} from feature work:
rather than demanding a green lint and a passing suite after every
edit (which would slow the describe--observe--refine loop of
Pattern~2), the developer lets small inconsistencies accumulate and
then clears them in a dedicated pass.
This mirrors the system prompt's own division of labor, which asks the
agent to run impacted tests after a change but reserves the full
\texttt{uv run check -{}-full} sweep for the pre-finish verification
stage.
Second, the ``find all bugs, redundancies, and inconsistencies''
phrasing invokes the File Browsing protocol: the agent surveys an
entire directory, writes a structured inventory of issues, and only
then proposes fixes---an explicit collect-then-act discipline that
prevents premature, locally-scoped patches.
Third, the qualifier ``fix tests only if there is no bug in the
code---report the bugs'' is a guardrail against a well-known
failure mode in which an agent makes a failing test pass by weakening
its assertions rather than by fixing the underlying defect.
By instructing the agent to \emph{report} rather than silently
``fix'' a test, the developer keeps the test suite an honest oracle.

%......................................................................
\subsection{Pattern 4: Paper--Code Co-Evolution}
\label{sec:p-paper}
%......................................................................

The system prompt and the paper describing it evolved together.
A change to the system prompt triggered a paper update, and a paper
revision sometimes triggered a code change:

\begin{itemize}[nosep]
  \item ``\texttt{SYSTEM.md} has changed.  Update and build the paper.''
        (Tasks~84, 167, 233, 261, 274, 312, 665, 693, 766, 927, 931, 1007).
  \item ``Can you check the consistency and correctness of the paper
        against itself and the latest code?''
        (Tasks~169, 694, 824, 985, 1009).
  \item ``I have fixed typos in the system prompt in the paper.
        Can you update \texttt{SYSTEM.md}?''
        (Task~700).
\end{itemize}

This bidirectional flow means the paper is always a faithful
description of the system, and the system always reflects the
principles claimed in the paper.
The phrase ``build the paper'' appears in 73~tasks, making
paper~maintenance one of the highest-volume non-coding activities in
the log; the \LaTeX{} toolchain (\texttt{pdflatex}, BibTeX) is
consequently one of the most-exercised pieces of the software
ecosystem catalogued in Section~\ref{sec:software}.

The co-evolution is genuinely bidirectional, and the log shows both
directions.
In the code-to-paper direction, a change to \texttt{SYSTEM.md} (the
system prompt) triggers a task of the form ``\texttt{SYSTEM.md} has
changed---update and build the paper,'' so that the paper's system-prompt
section never drifts from the deployed prompt.
In the paper-to-code direction, Task~700---``I have fixed typos in the
system prompt in the paper.  Can you update \texttt{SYSTEM.md}?''---uses
the paper as the source of truth and propagates an edit back into the
running system.
The consistency-audit tasks (``check the consistency and correctness
of the paper against itself and the latest code'') close the loop:
because the same agent can read both the \LaTeX{} source and the code
it describes, a divergence between claim and implementation is
mechanically detectable rather than relying on the author's memory.
This is the self-hosting principle (Section~\ref{sec:self-hosting})
applied to documentation: the artifact that describes the system is
maintained by the system, so it stays accurate as a side effect of
ordinary development.

%......................................................................
\subsection{Pattern 5: Architecture Investigation Before Change}
\label{sec:p-investigate}
%......................................................................

Before making non-trivial changes, the developer asked the agent to
explain the current architecture:

\begin{itemize}[nosep]
  \item ``Can you show me the detailed step-by-step workflow of
        \texttt{web\_server.py}?'' (Task~444).
  \item ``What happens when two tasks are run simultaneously?''
        (Tasks~3, 5, 7).
  \item ``How does the frontend and backend interact when a task is
        running?'' (Task~1818).
  \item ``Can you create a graph diagram showing how the server-side
        files are related?'' (Tasks~1024--1027).
\end{itemize}

This ``understand before you change'' discipline prevents blind
modifications.
The agent reads the code, produces a step-by-step explanation, and
the developer uses that understanding to formulate a precise change
request.
The pattern is so habitual that several investigation prompts recur
verbatim: ``can you explain step-by-step in details of the worktree
workflow?'' and ``can you tell me in very details what happens when a
task with sub agents is load''ed both appear multiple times in the
\texttt{frequent\_tasks} table.

The investigation step pays off precisely because the agent's
explanation and the agent's subsequent edits are produced by the same
reader of the same code.
When the developer asks ``what happens, step by step, with git in
\texttt{worktree\_sorcar\_agent.py} when a task finishes?'' and then,
in the next task, asks for a redesign of that lifecycle, the redesign
is grounded in the explanation the agent just generated---there is no
translation loss between a human's understanding of a design document
and the code that implements it.
This is the conversational form of the system prompt's pre-flight
``read before you write'' rule (Section~\ref{sec:preflight}):
the developer front-loads comprehension into an explicit
question-and-answer turn, so the change request that follows can be
stated as a precise, local edit rather than a vague aspiration.
The graph-diagram requests (Tasks~1024--1027) are a visual variant of
the same impulse: before reorganizing the server-side modules, the
developer asks the agent to render their dependency structure, turning
an implicit mental model into an inspectable artifact.

%......................................................................
\subsection{Pattern 6: System Prompt Engineering}
\label{sec:p-prompt}
%......................................................................

About 100~tasks were devoted to refining the system prompt itself:

\begin{itemize}[nosep]
  \item ``Can you check \texttt{SYSTEM.md} and tell me if you
        understand all instructions?  How can they be improved?''
        (Tasks~972--974, 1003--1006).
  \item ``You are not visiting at least 30~websites when you need
        to search.  Fix \texttt{SYSTEM.md}.''
        (Task~757).
  \item ``You are creating too many temporary files.  Improve
        \texttt{SYSTEM.md}.''
        (Task~1416).
  \item ``Can you look at yesterday's tasks and check which
        instructions are not being followed?  Fix them.''
        (Tasks~1267, 1269, 1271).
\end{itemize}

The developer treated the system prompt as production code:
observing the agent's behavior, identifying deviations from the
specification, and patching the prompt accordingly.
This is the prompt-engineering equivalent of a test-driven
development cycle.

What makes this pattern distinctive is that the test data is the
usage log itself.
Because every task and its full trajectory are persisted in
\texttt{sorcar.db}, the developer could ask the agent to mine its own
recent history for compliance failures: ``Look at yesterday's tasks
and check which instructions in \texttt{SYSTEM.md} are not being
followed.''
The agent reads the \texttt{events} table for the relevant tasks,
detects deviations (\eg{} a research task that fetched pages with
\texttt{curl} instead of \texttt{go\_to\_url}, or a code change that
skipped \texttt{uv run check}), writes an integration test with a
real LLM call to confirm the deviation reproduces, and only then
patches the prompt.
This is mutation testing applied to a specification: the developer
checks whether the prompt is strong enough to prevent an
\emph{observed} failure, not merely a hypothetical one.
The verbatim audit prompt---``can you check \texttt{PWD/src/kiss/
SYSTEM.md} and tell me if you understand all the instructions''---recurs
as a periodic self-review.
The fixes that resulted are visible in the deployed prompt today: the
``temporary files in \texttt{PWD/tmp/}'' rule, the explicit
\texttt{curl}/\texttt{wget} prohibition in the web-research section,
and the enumerated file extensions that trigger the mandatory
\texttt{uv run check} were all added reactively after the log revealed
the corresponding evasions.

%......................................................................
\subsection{Pattern 7: Multi-Channel General Assistance}
\label{sec:p-general}
%......................................................................

Beyond software engineering, the developer used \kisssys{} as a
general-purpose assistant:

\begin{itemize}[nosep]
  \item \textbf{Smart home:} ``Turn off living room and family room
        lights'' via the Govee API (Tasks~1181--1219).
  \item \textbf{Travel:} ``Plan me a trip to Yosemite'' with hotel
        availability checks (Tasks~911, 922--923, 926, 930, 932, 937).
  \item \textbf{Weather:} ``How is the weather today?''
        (Tasks~359, 365, 405, 422, 698, 727--728, 767, 875--876).
  \item \textbf{Shopping:} ``Where can I find Darjeeling tea in the
        Bay Area?'' (Tasks~789--790), ``Where should I buy Louis
        Vuitton bags?'' (Task~774).
  \item \textbf{Finance:} ``Will Microsoft stock increase by August
        2026?'' (Tasks~333, 337), ETF analysis (Tasks~777--778,
        1111--1112, 1123, 1178--1180, 1222).
  \item \textbf{Communication:} Slack messages (Tasks~299--301,
        913--915, 1015--1017, 1188--1189),
        iMessage (Tasks~550--551, 1184--1185, 1210),
        Gmail (Tasks~1191--1198, 1233).
  \item \textbf{Ethical refusal:} ``Can you hack the Echo Show~15?''
        The agent refused and offered five legitimate
        alternatives (Task~1240).
\end{itemize}

This pattern demonstrates that the same system prompt and
architecture serve both engineering and non-engineering tasks.
The KISS principle---one agent, one prompt, one architecture---scales
across domains.

The mechanism that makes this possible is the third-party agent
interface (Section~\ref{sec:software}): smart-home control, Slack,
iMessage, and Gmail are all Python modules in
\texttt{kiss/agents/third\_party\_agents}, and the Sorcar Agent
invokes them through the same uniform tool interface it uses for
\texttt{Bash}, \texttt{Edit}, and \texttt{go\_to\_url}.
No special routing, planner, or domain classifier sits in front of
them; the model selects the right tool from the task description
alone.
The log even records the bootstrapping of these integrations as
ordinary tasks---``can you authenticate with govee.com so that you
can control the lights?'' and ``do whatever is necessary to control
the lights of govee.com''---after which day-to-day commands such as
``use \texttt{govee.py} to turn off family room lights'' (which
appears repeatedly in the \texttt{frequent\_tasks} table) just work.
The system prompt's own override section anticipates this:
``Authenticate unauthenticated third-party agents; ask the user only
when a page requires human authentication,'' so the agent provisions
its own credentials and only interrupts the developer for a genuine
human-in-the-loop login.

\paragraph{The same rigor applies off-task.}
Notably, the non-coding tasks inherit the engineering discipline.
A weather or stock query triggers the Web Research protocol---the
agent visits multiple sources, records them in a
\texttt{tmp/information-\{id\}.md} file, and is forbidden from
answering current-events questions from stale training data.
A research request such as ``Research these three topics and
summarize each\ldots'' (a recurring multi-topic prompt in the log) is
handled with the same collect-then-synthesize rigor as a code
investigation.
Even the ethical refusal in Task~1240 is an application of the
defensive-programming clause (Section~\ref{sec:defensive}): the agent
declined to hack the Echo Show~15 and offered five legitimate
alternatives, treating ``refuse what you cannot do safely'' as a
first-class behavior rather than an exception.
The lesson of Pattern~7 is therefore not merely that one agent can do
many things, but that the \emph{same} engineering safeguards---verify
sources, isolate changes, refuse unsafe requests, never fabricate---apply
uniformly whether the task is a code fix or a dinner reservation.

%----------------------------------------------------------------------
\section{Principles Behind the Patterns}
\label{sec:principles}
%----------------------------------------------------------------------

Each usage pattern maps to one or more established software
engineering principles.

%......................................................................
\subsection{The KISS Principle}
\label{sec:kiss}
%......................................................................

\emph{Keep it simple.}
The five-layer hierarchy embodies this: 3,346~lines total,
an order of magnitude smaller than comparable systems.
Pattern~7 (multi-channel assistance) shows the principle at the
usage level: one system handles coding, smart home, travel, and
communication without specialized sub-systems.

When the user typed ``hi'' (Tasks~207, 272, 278, 285, 289, 416,
421, 443, 454, \ldots---roughly 150~occurrences), the agent
responded with a single friendly sentence.
It did not launch into a capabilities description.
The KISS principle applied to interaction design says: match the
weight of the response to the weight of the input.

%......................................................................
\subsection{Separation of Concerns}
\label{sec:separation}
%......................................................................

\emph{Each module addresses a single concern.}
Pattern~2 (iterative feature construction) relies on this:
the remote web server feature touched the Sorcar Agent
(tool integration), the Chat Sorcar Agent (persistence), and the
Worktree Sorcar Agent (git isolation), but each change was scoped
to one layer.

The smart-home example (Pattern~7) exercised separation at
multiple levels: the Chat Sorcar Agent loaded conversation context,
the Sorcar Agent selected the Govee tool, and the KISS Agent
tracked the budget---each layer unaware of the others' concerns.

%......................................................................
\subsection{Test-First Development}
\label{sec:test-first}
%......................................................................

\emph{Write a failing test, then make it pass.}
Pattern~1 (test-first bug fixing) is the direct application.
The phrase ``write an integration test to reproduce the issue, then
fix it'' appears in hundreds of tasks.
The system prompt reinforces this with: ``Do not use mocks, patches,
fakes, or test doubles.''

Pattern~3 (periodic code hygiene) extends this to maintenance:
running the full test suite after every batch of changes ensures
that the cumulative effect of many small edits does not break the
system.

%......................................................................
\subsection{Defensive Programming}
\label{sec:defensive}
%......................................................................

\emph{Validate everything.  Refuse what you cannot do safely.}
The ethical refusal in Pattern~7 (Task~1240) is the clearest example.
The agent refused to hack the Echo Show~15 and offered five
alternatives.

Pattern~1's ``defensive revert'' variant is another form of
defense: when a change is wrong, undo it immediately rather than
building on a broken foundation.
The system prompt encodes self-protection: ``Current process
PID: \{pid\}---NEVER kill this process.''

%......................................................................
\subsection{Pre-Flight Checks}
\label{sec:preflight}
%......................................................................

\emph{Read before you write.}
Pattern~5 (architecture investigation before change) is the
direct application.
The developer asked ``what happens when\ldots'' and ``show me
the workflow'' before issuing change requests.

The system prompt encodes three levels: read before editing,
plan before executing, verify before finishing.
Pattern~3's periodic ``\texttt{uv run check --full and fix}''
is the automated form of the pre-finish verification.

%......................................................................
\subsection{Self-Hosting as Continuous Integration}
\label{sec:self-hosting}
%......................................................................

\emph{Use the system to build the system.}
Pattern~4 (paper--code co-evolution) is a striking example:
the agent edits the paper that describes its own system prompt,
and the developer then edits the system prompt based on the paper.
Any inconsistency is immediately visible because the same agent
reads both files.

Self-hosting caught bugs that external testing missed.
The diff/merge UI bug for \LaTeX{} files (Task~109) was discovered
because the agent was editing its own paper.
The auto-commit bug (Task~104) was discovered because the developer
was reviewing the agent's own output.

%----------------------------------------------------------------------
\section{The Software Ecosystem}
\label{sec:software}
%----------------------------------------------------------------------

The 3,099~tasks touched a broad software ecosystem.
Table~\ref{tab:software} lists the tools and services used,
grouped by function.

\begin{table}[t]
\centering
\caption{Software used by the developer through \kisssys{}
over the 44-day period.}
\label{tab:software}
\begin{tabular}{ll}
\toprule
\textbf{Function} & \textbf{Software} \\
\midrule
IDE / editor          & VS~Code (TypeScript extension) \\
Languages             & Python, TypeScript, JavaScript, \\
                      & CSS, HTML, \LaTeX{} \\
Package management    & uv (Python), npm (Node.js) \\
Version control       & Git, GitHub \\
Testing               & pytest (with coverage) \\
Linting / type-check  & \texttt{uv run check --full} \\
Document preparation  & pdflatex, BibTeX \\
Slides                & python-pptx (PowerPoint) \\
Database              & SQLite (\texttt{sorcar.db}) \\
Browser automation    & Playwright, Chromium \\
Remote access         & Cloudflare Tunnels, TLS/WSS \\
Notifications         & ntfy.sh \\
Containerization      & Docker (Terminal Bench~2.0) \\
Smart home            & Govee API (third-party agent) \\
Messaging             & Slack, iMessage, WhatsApp (agents) \\
Email                 & Gmail API, Resend \\
Scheduling            & cron (via \texttt{cron\_manager\_daemon}) \\
Video editing         & Final Cut Pro \\
\bottomrule
\end{tabular}
\end{table}

Two observations stand out.
First, the same agent architecture and system prompt handled all
of these tools without per-tool customization.
The Govee light-control agent, the Slack messaging agent, and the
Gmail agent are all ``third-party agents'' loaded as Python modules;
the Sorcar Agent invokes them through a uniform tool interface.

Second, the developer's workflow was not purely software engineering.
Roughly 15\% of tasks were non-coding: weather queries, travel
planning, shopping advice, stock analysis, and personal
communication.
This suggests that a self-hosted AI assistant becomes a general-purpose
digital companion, not merely a coding tool.

%----------------------------------------------------------------------
\section{The System Prompt as Engineering Specification}
\label{sec:system-prompt}
%----------------------------------------------------------------------

The system prompt is a structured specification of engineering
practices, organized into XML-tagged sections:

\begin{lstlisting}[style=prompt]
<identity>      -- who the agent is
<visibility_constraint> -- what the user sees
<tool_rules>    -- how to use tools
<web_research>  -- how to research
<code_style>    -- how to write code
<workflow>      -- pre-flight, deep work, planning
<testing>       -- test discipline
<pre_finish_verification> -- exit checklist
<sorcar_specific> -- project overrides
\end{lstlisting}

Each section encodes a principle from Section~\ref{sec:principles}.
Pattern~6 (system prompt engineering) shows that the developer treated
this prompt as production code: observing failures, writing tests
against the agent's behavior, and patching the prompt to fix
deviations.

\paragraph{Prompt as test oracle.}
The developer repeatedly asked the agent to audit its own compliance:
``Look at yesterday's tasks and check which instructions in
\texttt{SYSTEM.md} are not being followed.  Create an integration
test with a real LLM call to confirm each issue.  Then fix
\texttt{SYSTEM.md}.'' (Tasks~1267, 1269, 1271).
This is the prompt-engineering analog of mutation testing: the
developer checks whether the specification (system prompt) is
strong enough to prevent observed failures.

\paragraph{Prompt evolution.}
Over 44~days, the system prompt evolved from aggressive imperatives
(``BE RELENTLESS'') to calm, explanatory framing (``Be rigorous,
check facts, and produce high-quality work'').
Specific instructions were added reactively: the ``temporary files
in \texttt{PWD/tmp/}'' rule (Task~1416) was added after the agent
polluted the project root; the ``visit at least 10~websites'' rule
(Task~757) was strengthened after the agent cut research short.

%----------------------------------------------------------------------
\section{Evaluation}
\label{sec:evaluation}
%----------------------------------------------------------------------

We evaluate on Terminal Bench~2.0, a benchmark of 89~diverse
terminal-based programming tasks.
Each task runs in an isolated Docker container with automatic
verification.
We use Claude Opus~4.6 as the underlying model and run five trials
per task.
We do not modify the general system prompt or inject
benchmark-specific instructions.

\begin{table}[t]
\centering
\caption{Terminal Bench~2.0 aggregate results (89 tasks, 5 trials,
Claude Opus~4.6).}
\label{tab:results}
\begin{tabular}{lc}
\toprule
\textbf{System} & \textbf{Pass Rate} \\
\midrule
Claude Code       & 58.0\% \\
Cursor Composer~2 & 61.7\% \\
\kisssys{}        & 62.2\% \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:results} shows the results.
\kisssys{} achieves a 62.2\% overall pass rate (277 of 445 trials).
The pass@any rate is 78.7\% (70/89).
The pass@all rate is 43.8\% (39/89).
The median cost per trial is \$0.45; the mean is \$0.90.

%----------------------------------------------------------------------
\section{Discussion}
\label{sec:discussion}
%----------------------------------------------------------------------

\subsection{What the Patterns Reveal}

The seven patterns tell a consistent story.
The developer did not write specifications or design documents.
Instead, the developer \emph{conversed} with the agent, issuing
short natural-language commands and observing results.
The engineering discipline was embedded in the conversation style:
always ask for a test first, always investigate before changing,
always run the full suite after a batch of changes, always revert
immediately when something goes wrong.

This suggests that in an AI-assisted development workflow, the
developer's role shifts from \emph{writing code} to
\emph{directing and verifying} an agent that writes code.
The engineering principles do not change; they are expressed
through task phrasing rather than code structure.

\subsection{Strunk and White for Prompts}

Strunk and White~\cite{strunkwhite2000} advise: ``Omit needless
words.''
Early versions of the system prompt used aggressive imperatives.
These were replaced with calm, explanatory framing.
The agent performed better with the latter.

Each instruction names a specific action, a specific failure mode
it prevents, and a specific verification method.
The pattern of prompt refinement (Section~\ref{sec:p-prompt})
shows that this clarity was achieved iteratively, not designed
upfront.

\subsection{The Self-Hosting Paradox}

Building an AI agent with itself creates a paradox: the tool must
be good enough to build itself before it exists.
We resolved this through bootstrapping: the first version was
written manually, and each subsequent version was written with
the previous one.

The 30+ defensive reverts in the log (Pattern~1) show the cost of
this approach: roughly one in every 90~tasks required undoing the
agent's work.
But the benefit is that every surviving change has been validated
by the same system that will maintain it.

\subsection{General-Purpose Use}

The non-coding tasks (Pattern~7) reveal an unexpected benefit of
self-hosting: because the developer uses the system all day, it
becomes the natural interface for all tasks, not just coding.
Weather, travel, shopping, messaging, and smart-home control all
flow through the same chat interface.
This validates the KISS principle at the product level:
one tool for everything beats many specialized tools.

%----------------------------------------------------------------------
\section{Threats to Validity}
\label{sec:threats}
%----------------------------------------------------------------------

\textbf{Single developer.}
All 3,099~tasks were issued by one developer.
Other developers may exhibit different patterns.

\textbf{Single system.}
The patterns are specific to \kisssys{}.
Different agent architectures may induce different workflows.

\textbf{Self-hosting bias.}
Because the system was built with itself, the architecture is
optimized for the kinds of tasks the agent can already do well.

\textbf{Single benchmark.}
We evaluate on Terminal Bench~2.0 only.

%----------------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}
%----------------------------------------------------------------------

We analyzed 3,099~tasks from 44~days of building \kisssys{} with
\kisssys{}.
Seven patterns emerged: test-first bug fixing, iterative feature
construction, periodic code hygiene, paper--code co-evolution,
architecture investigation before change, system prompt engineering,
and multi-channel general assistance.

Each pattern maps to an established software engineering principle:
test-driven development, separation of concerns, defensive
programming, pre-flight checks, the KISS principle, and self-hosting
as continuous integration.

The developer used \kisssys{} to write code in five languages,
control smart-home lights, plan trips, send messages, check email,
query weather and stocks, build a website, prepare lecture slides,
and refuse an unethical request---all through the same 3,350-line
agent framework and a single structured system prompt.

The surprise is not the principles.
They are decades old.
The surprise is that encoding them in a system prompt and a simple
layered architecture produces an AI assistant that works well
enough to build itself---and to do everything else the developer
needs.

%----------------------------------------------------------------------
% References
%----------------------------------------------------------------------

{ \small

\bibliographystyle{plainnat}
\bibliography{se_kiss_sorcar}
}

\end{document}
