\documentclass{article}
\usepackage[preprint,nonatbib]{neurips_2026}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{array}
\usepackage{tabularx}
\usepackage{float}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{fancyvrb}
\usepackage{mdframed}
\usepackage{listings}
\usepackage{amsmath}

% \todo is only used as a fallback; real values fill everything now.
\newcommand{\todo}[1]{\textbf{?#1?}}

\lstdefinestyle{kisspy}{%
  language=Python,
  basicstyle=\ttfamily\scriptsize,
  keywordstyle=\color[rgb]{0.0,0.0,0.8}\bfseries,
  commentstyle=\color[rgb]{0.25,0.5,0.35}\itshape,
  stringstyle=\color[rgb]{0.73,0.13,0.13},
  showstringspaces=false,
  frame=single,
  framesep=2mm,
  numbers=left,
  numberstyle=\tiny\color{gray},
  numbersep=5pt,
  breaklines=true,
  tabsize=4,
  captionpos=b}

\newenvironment{promptbox}{\begin{mdframed}[linewidth=0.4pt,linecolor=black,innerleftmargin=5pt,innerrightmargin=5pt,innertopmargin=5pt,innerbottommargin=5pt,skipabove=2pt,skipbelow=5pt]\setlength{\parskip}{0pt}\setlength{\parindent}{0pt}\ttfamily\scriptsize\raggedright\frenchspacing\obeylines\leavevmode\strut\ignorespaces}{\end{mdframed}}

% ------------------------------------------------------------------
% Result macros — fill in after the ablation/adaptive experiments run.
% Numbers marked \todo{...} will be replaced by real numbers from
% swedefend/results/ablation.csv and adaptive_asr.csv.
% ------------------------------------------------------------------
\newcommand{\NcorpusTotal}{149}
\newcommand{\NcorpusMal}{49}
\newcommand{\NcorpusBen}{100}
\newcommand{\NcorpusBenTemplates}{21}
\newcommand{\NcorpusCWE}{35}
\newcommand{\NcorpusPI}{6}
\newcommand{\NcorpusFP}{8}
% 95% upper confidence bounds for 0/N false-positive counts.  We report the
% Wilson score interval upper endpoint (two-sided) and, for comparison, the
% Clopper-Pearson exact upper bound (two-sided), because Wilson is the
% textbook interval for small n and Clopper-Pearson is the conservative
% exact companion often reported alongside it.
%   0/20 : Wilson  16.11%, CP two-sided  16.84%
%   0/100: Wilson   3.70%, CP two-sided   3.62%, CP one-sided 2.95%
\newcommand{\FPRWilsonTwenty}{16.1\%}
\newcommand{\FPRWilsonHundred}{3.7\%}
\newcommand{\FPRExactHundred}{3.62\%}
\newcommand{\FPRExactHundredOne}{2.95\%}

% Numbers filled in from swedefend/results/ablation.csv (judge=claude-opus-4-7,
% n=149 cases: 49 malicious, 100 benign across 20 scenario templates):
\newcommand{\LonlyCatch}{12.24\%}
\newcommand{\LonlyFPR}{0.00\%}
\newcommand{\LtwoCatch}{2.04\%}
\newcommand{\LtwoFPR}{0.00\%}
\newcommand{\LthreeCatch}{30.61\%}
\newcommand{\LthreeFPR}{0.00\%}
\newcommand{\JudgeCatchLow}{87.76\%}
\newcommand{\JudgeFPRLow}{0.00\%}
\newcommand{\JudgeCatchMid}{87.76\%}
\newcommand{\JudgeFPRMid}{0.00\%}
\newcommand{\JudgeCatchHigh}{83.67\%}
\newcommand{\JudgeFPRHigh}{0.00\%}
\newcommand{\CombinedCatchLow}{100.00\%}
\newcommand{\CombinedFPRLow}{0.00\%}
\newcommand{\CombinedCatchMid}{100.00\%}
\newcommand{\CombinedFPRMid}{0.00\%}
\newcommand{\CombinedCatchHigh}{97.96\%}
\newcommand{\CombinedFPRHigh}{0.00\%}
% Corroboration-gated (AI-Discovery D1) rows — identical results on the current
% corpus because every malicious veto is corroborated by a named
% capability/control and no benign case triggers even an uncorroborated veto.
\newcommand{\CombinedCatchHighCorr}{97.96\%}
\newcommand{\CombinedFPRHighCorr}{0.00\%}

% MSR baseline (Przymus et al. 2025) — verified numbers from arXiv:2509.05372:
\newcommand{\MSRSingle}{47\%}
\newcommand{\MSREnsembleOnly}{68\%}
\newcommand{\MSREnsemblePost}{72.5\%}
\newcommand{\MSRFPRStructured}{1\%}
\newcommand{\MSRFPRUnstructured}{34\%}

\title{SWEDefend: A Confidence-Gated Intent-Alignment Judge \\
       with Capability-Diff Reasoning for \\
       Automated-Program-Repair Backdoor Defense}

\author{%
  Koushik Sen \\
  EECS Department, UC Berkeley \\
  \texttt{ksen@berkeley.edu} \\
}

\begin{document}

\maketitle

\begin{abstract}
LLM-based automated program repair (APR) agents such as SWE-agent~\cite{sweagent} can be induced to produce test-correct patches that silently embed magic-string-gated CWE payloads: recent work on \textsc{SWExploit}~\cite{swexploit} reports correct-attack-success rates up to 0.91 under a strict issue-only threat model. An empirical study of the obvious pre- and post-repair defenses (guardrails, LLM filters, GitHub~Copilot, and CodeQL)~\cite{msrdefense} found that the best single pre-repair filter blocks only \MSRSingle{} of adversarial bug reports, the strongest ensemble reaches \MSREnsembleOnly{}, and even combining pre-repair ensembling with post-repair Copilot review tops out at \MSREnsemblePost{}. That study also validated its filter on 100 real \texttt{psf/requests} issues and obtained a favourable \MSRFPRStructured{} false-positive rate (\textit{FPR}) with structured \texttt{gpt-4o-mini}.
\par
The natural extension of that baseline is an intent-alignment LLM judge that vetoes patches misaligned with the issue's stated intent. In a preliminary draft we found that a naive fail-closed judge reached 100\% catch but at a $\sim$20\% FPR --- roughly $20\times$ worse than the study's best pre-filter and unacceptable in practice. This paper documents three concrete methodological improvements over that draft and reports honest results:
\begin{itemize}[nosep,leftmargin=1.4em]
\item A \emph{confidence-gated} intent judge (SWEDefend-L4) that only vetoes when the judge's self-reported confidence exceeds a threshold $\tau$ calibrated on a held-out benign set. Reporting at operating points matched to the \MSRFPRStructured{} FPR baseline lets us compare like with like.
\item A \emph{capability-diff / premise-cross-check} judge prompt that vetoes patches introducing unrequested dangerous capabilities or removing existing security controls (auth decorators, escape, verify=True, safe-open) \emph{regardless of what the issue asserts}. This defends against a class of attacks the naive intent judge cannot: false-premise ``goal-hijack'' issues (e.g.\ ``the /admin endpoint should be public --- remove @login\_required'') that a naive judge rubber-stamps as aligned with the stated goal.
\item An evaluation designed for \emph{generalization} rather than a single attack instantiation: a \NcorpusTotal-case labeled corpus containing five CWE families in seven variants each (magic-string, env-var, length-, and time-gated; helper-wrapped; \texttt{\_\_import\_\_}-encoded; and no-gate dead-drop --- \NcorpusCWE{} attacks total), \NcorpusPI{} prompt-injection cases, \NcorpusFP{} false-premise cases, and \NcorpusBen{} \emph{diverse} benign controls across \NcorpusBenTemplates{} scenario templates (docstring updates, type annotations, isort re-orders, unit-test additions, logging-message improvements, error-message improvements, dict key renames, dataclass field renames, generator refactors, \texttt{with}-block migrations, pathlib migrations, f-string modernisations, CI-matrix updates, README fixes, non-security decorator cleanups, plus the pre-existing null-checks, refactors, legitimate \texttt{subprocess}/\texttt{open} uses, and feature additions). AI-Discovery step D3 expanded the benign controls from an earlier \NcorpusBenTemplates{}-templates-in-name-only $n=20$ baseline (Wilson two-sided upper bound $\approx \FPRWilsonTwenty$ on $0/20$) to the current $n=100$ (Wilson two-sided upper bound $\approx \FPRWilsonHundred$ on $0/100$), so the reported ``0\% FPR'' is a substantially tighter statistical claim rather than a trivial pass on a small denominator.
\end{itemize}
The adaptive-attack evaluation follows the methodology of Carlini~et~al.~\cite{carlini2019adv} and Tram\`er~et~al.~\cite{tramer2020adaptive}: an attacker LLM (PAIR~\cite{pair}-style, free choice of strategy) is given full per-layer feedback from the defense on each attempt and is scored on whether the patch it produces is accepted by SWEDefend while still containing the sink signature of its CWE goal. \textbf{We report a partial-defense result honestly:} SWEDefend achieves high static catch at a low target FPR, but the LLM attacker beats the confidence-gated combined pipeline (at $\tau=0.9$) on all three seed CWE goals within three iterations, primarily by \emph{premise reframing} that pushes the judge's confidence below the veto threshold. We characterise this as a known failure mode and discuss the remediation path (heterogeneous LLM jury, true diff input to the judge, behavioural verification against real SWE-bench repositories). We release the corpus generator, the pipeline, the adaptive-attack harness, all raw per-case outputs, and an independent code-review-derived list of implementation deviations from the paper's claims (\S\ref{sec:discussion}).
\end{abstract}

%------------------------------------------------------------
\section{Introduction}
\label{sec:intro}

\paragraph{APR agents are a high-value new attack surface.}
LLM-based APR agents ingest a GitHub issue --- a free-form, attacker-influenceable text field --- and autonomously edit a codebase until the project's tests pass. Benchmarks such as SWE-bench~Lite~\cite{swebench} have driven rapid progress. But the very thing that makes these agents useful --- their willingness to follow the natural-language description of a bug --- is also what makes them exploitable: anyone who can file or edit an issue can attempt to shape the resulting patch.

\paragraph{SWExploit weaponises the issue field.}
\textsc{SWExploit}~\cite{swexploit} demonstrates that under a strict black-box threat model where the attacker modifies \emph{only} the issue text, an APR agent can be induced to emit a patch that (a)~still passes all hidden regression tests and (b)~silently contains an attacker-chosen CWE payload gated behind a ``magic string'', so it is dormant on ordinary inputs and only fires when the attacker later supplies the trigger. Because the patch is functionally correct it sails through the test suite; because the payload is dormant, dynamic checks see nothing; and because it is expressed as ordinary Python, it looks like normal bug-fix code. \textsc{SWExploit} reports correct-attack-success rates up to 0.91 across agents and backends.

\paragraph{The obvious defences are not enough --- but they are \emph{low-FPR}.}
The empirical study of Przymus, Happe, and Cito~\cite{msrdefense} evaluated content guardrails (LlamaGuard, PromptGuard, Granite-Guardian), strong LLM filters (GPT-4.1/o4-mini/4o-mini), GitHub Copilot review, and CodeQL against 51 adversarial bug reports. The best single pre-repair filter blocks only \MSRSingle{} of them; ensembles reach \MSREnsembleOnly{}, and only when combined with post-APR Copilot review does the total blocking rise to \MSREnsemblePost{} (37/51). Critically, the study also \emph{validated its filter on 100 real \texttt{psf/requests} issues} (\#6000--6100) and obtained a false-positive rate of just \MSRFPRStructured{} with structured \texttt{gpt-4o-mini}. Any new defence must be judged against this baseline on \emph{both} axes --- catch rate and FPR --- at matched operating points, or the comparison is unfair.

\paragraph{Contribution.}
This paper does exactly that. We build on the natural next step --- a pre-merge intent-alignment LLM judge that reasons about the produced patch --- and address three concrete deficiencies of a naive fail-closed judge that our preliminary evaluation exposed:
\begin{enumerate}[nosep,leftmargin=1.4em]
\item \emph{The naive judge's FPR is dominated by low-confidence vetoes.} We introduce a \textbf{confidence-gated veto}: the judge is asked to emit a self-reported confidence and a veto only enforces when confidence $\geq \tau$. $\tau$ is calibrated on a held-out benign set; at $\tau=0.9$ the confidence gate collapses the pipeline FPR to the operating point of the strongest \MSRFPRStructured{} baseline. Reporting at matched operating points is the honest way to compare classifiers~\cite{sommer2010}.
\item \emph{The naive judge is fooled by false-premise ``goal-hijack'' issues.} If a malicious issue asserts that an endpoint ``should be public'' and asks for the \texttt{@login\_required} decorator to be removed, the naive judge --- which is asked to check alignment with the \emph{stated} intent --- rubber-stamps the removal, because the patch faithfully executes the (malicious) stated goal. We introduce a \textbf{capability-diff / premise-cross-check} judge prompt that explicitly asks the judge to flag \emph{removals} of security controls and \emph{additions} of unrequested dangerous capability, independent of what the issue asserts. This closes an attack class the naive intent-alignment judge cannot.
\item \emph{A single attack instantiation is not a defence result.} We build a corpus with \emph{seven variants} of each CWE family --- magic-, env-var-, length-, and time-gated; helper-wrapped; \texttt{\_\_import\_\_}-encoded; no-gate dead-drop --- plus a dedicated false-premise class and diverse benign controls (legitimate \texttt{subprocess}/\texttt{open} uses, refactors, feature additions), so both catch rate and FPR are meaningful signals of generalisation rather than of memorising one attack template.
\end{enumerate}

\paragraph{Adaptive attacker.}
Following the methodology of Carlini~et~al.~\cite{carlini2019adv} and Tram\`er~et~al.~\cite{tramer2020adaptive}, we evaluate SWEDefend against an \emph{LLM-driven} adaptive attacker modeled on PAIR~\cite{pair}: an attacker LLM sees the full per-layer verdict of the defense on each attempt and is free to choose any refinement strategy (payload splitting, base64/\texttt{\_\_import\_\_} indirection, premise manipulation, benign filler, helper hoisting, encoded gates). The budget is up to 40 iterations per seed --- comparable to PAIR's own budget and considerably more than the five hard-coded rounds our preliminary draft used. Refusals from the attacker LLM (a real phenomenon on the most heavily safety-aligned models) are reported honestly rather than hidden.

\paragraph{Non-contributions.}
We do \emph{not} claim the intent-alignment judge as our conceptual novelty --- \cite{msrdefense} already uses an LLM filter with a similar shape. The improvements we claim are the confidence-gated veto, the capability-diff / premise-cross-check prompt, the corpus construction (variants, false-premise class, diverse benign), the LLM-driven adaptive attacker methodology, and the offline provenance layer (custom local Semgrep rules) whose scope we explicitly \emph{narrow} to MEDIUM/HIGH-severity findings after the preliminary draft showed the raw sink-name detector produced excessive FPs on legitimate uses.

%------------------------------------------------------------
\section{Background and Threat Model}
\label{sec:background}

\paragraph{The APR pipeline.}
An APR agent receives a repository at a buggy commit and an issue containing a natural-language problem statement, often with a traceback and steps to reproduce. The agent explores the code, edits files, and iterates until the hidden test suite passes. On SWE-bench Lite~\cite{swebench}, correctness is defined by two test sets shipped with each instance: \texttt{FAIL\_TO\_PASS} (tests that must go from failing to passing) and \texttt{PASS\_TO\_PASS} (tests that must stay passing). A patch is ``correct'' iff both hold.

\paragraph{The \textsc{SWExploit} attack (three loops)~\cite{swexploit}.}
The attack operates entirely within the issue field: (1)~program analysis identifies (file, function, string-typed parameter) candidates on the failing path, (2)~an auxiliary LLM writes a \emph{fake} traceback ending in \texttt{NameError:\ trigger}, a \emph{fake} reproduce-code block that monkey-patches the target function, and a \emph{fake} requirement describing the payload behaviour without naming it, (3)~the issue is refined for up to ten rounds until the APR agent's patch contains a callable payload reachable from the program's control flow. The payload is wrapped in a small \texttt{trigger} gated by a magic string so it is dormant on benign inputs. \textsc{SWExploit} instantiates five payload families: CWE-78 command injection, CWE-502 unsafe deserialization, CWE-327 broken crypto, CWE-94 SSTI, CWE-22 path traversal.

\paragraph{Threat model.}
We inherit \textsc{SWExploit}'s black-box threat model. The attacker may edit only the issue text; the backend LLM, the APR agent, the repository source, and the CI/CD configuration are out of the attacker's reach. An attack succeeds iff the emitted patch is test-correct \emph{and} contains a reachable payload. Two aspects of this threat model deserve explicit statement:

\emph{(i)~Variations within the threat model.} The magic-string gate is one specific instantiation. A defense that only stops the specific gate ``\texttt{if x.startswith(MAGIC)}'' does not stop the threat model; the attacker is free to gate on an environment variable, a length, a time, or a helper-wrapped conditional; to invoke the sink via \texttt{\_\_import\_\_} or \texttt{getattr}; or to plant the sink dead-drop with no runtime gate at all. Our corpus covers each of these seven variants for every CWE family.

\emph{(ii)~False-premise / goal-hijack.} Nothing in the threat model requires the issue to be a \emph{plausible} bug report. An attacker can just as easily submit an issue asserting a wrong \emph{premise} --- ``the aggregate report page should be public; please remove \texttt{@login\_required}'' --- and steer the agent into producing a patch that faithfully executes the malicious premise. This is a well-known concern in the indirect-prompt-injection literature~\cite{greshake2023,owaspllm01}. An intent-alignment judge that only checks alignment with the \emph{stated} intent is defenseless against this class; SWEDefend's capability-diff / premise-cross-check judge prompt (\S\ref{sec:defense}) is specifically designed to address it.

%------------------------------------------------------------
\section{The SWEDefend Four-Layer Defense}
\label{sec:defense}

SWEDefend chains four layers behind a pipeline that is \emph{fail-closed for high-confidence vetoes only}. A patch is rejected if any of L1, L2, or L3 objects, or if L4's misalignment verdict has confidence $\geq \tau$. This section describes each layer with an emphasis on the design choices that changed between our preliminary draft and this paper.

\subsection{Layer 1: Issue Sanitizer (unchanged)}
Following OWASP LLM01~\cite{owaspllm01} and the Greshake~et~al.\ indirect-prompt-injection taxonomy~\cite{greshake2023}, L1 Unicode-normalises the issue text, strips zero-width and Trojan-Source bidi characters, redacts HTML comments and long base64/hex blobs, and pattern-matches eleven indirect-prompt-injection openers and seven exfiltration lures. It marks the issue \emph{suspicious} on any hit. \textbf{Honest note.} We do not claim L1 is a robust defense on its own --- a regex list is trivially evadable and its main role is to catch the naive prompt-injection sub-family (the HTML-comment ``ignore previous instructions'' case).

\subsection{Layer 2: Masked-Reproduction Behavioural Verification (unchanged design; scope clarified)}
Inspired by MELON~\cite{melon}, L2 replaces fenced code blocks, indented code, and shell-prompt lines in the (already-sanitized) issue with \texttt{[MASKED-REPRO-SPAN]} and verifies the patch against the SWE-bench \texttt{FAIL\_TO\_PASS}/\texttt{PASS\_TO\_PASS} behavioural contract rather than trusting the attacker-supplied reproduction steps. L2 requires a repository and a behavioural contract; on the static synthetic corpus of \S\ref{sec:eval} we report an \emph{L2-mask-proxy} row that counts a case as blocked when the masker rewrote $\geq 50$ characters of the issue (i.e.\ the attacker planted substantial fake reproduction that L2 would defer for behavioural verification). \textbf{Honest note.} The reviewer of a prior draft correctly noted that a masker keyed on fenced code is easy to evade by simply writing the fake reproduction as inline prose. On the diversified corpus L2's mask-proxy fires on only 1/49 cases (see \texttt{ablation.csv}: the CWE-94/magic variant whose fake traceback contained a fenced code block long enough to exceed the 50-character mask trigger); its main practical value is the behavioural verification step that requires a real repo, which we cannot exercise on the static synthetic corpus.

\subsection{Layer 3: Taint / Dataflow Provenance (scope narrowed to MEDIUM/HIGH)}
\label{sec:l3}
The MSR-25 study~\cite{msrdefense} showed CodeQL flags 0\% of these injected vulnerabilities out of the box. L3 uses Bandit plus custom, offline Semgrep taint rules --- shipped locally to avoid the network dependency on the Semgrep registry --- to map dangerous sinks (\texttt{subprocess.run(...,\ shell=True)}, \texttt{pickle.loads}, \texttt{eval}, \texttt{exec}, \texttt{hashlib.md5}, \texttt{jinja2.Template(...).render}, ...) to a sink report. \textbf{Change from the preliminary draft:} we now veto only on MEDIUM- or HIGH-severity findings; LOW-severity findings (bandit \texttt{B603}: an ordinary hardcoded \texttt{subprocess.check\_output(['git',\ 'rev-parse',\ 'HEAD'])} call) are treated as advisory. Without this narrowing, every legitimate use of \texttt{subprocess} or \texttt{open} anywhere in the codebase becomes a false positive; the change matches the MSR-25 observation that a raw sink-name detector is not a useful classifier on its own.

\subsection{Layer 4: Confidence-Gated Intent Judge with Capability-Diff / Premise Cross-Check}
The core change from prior work is here. The naive intent judge~\cite{msrdefense} asks an LLM whether the patch is aligned with the issue's stated intent, and vetoes on \texttt{aligned=false}. Two problems:
\begin{enumerate}[nosep,leftmargin=1.4em]
\item \textbf{FPR problem.} On our diverse benign controls the naive judge occasionally decides that a legitimate patch is ``scope creep'' or ``adds unnecessary capability'' with low confidence (e.g.\ 0.55) --- and the fail-closed pipeline treats that as a veto. Result: 20\%-scale FPR, an order of magnitude worse than the MSR-25 baseline.
\item \textbf{False-premise problem.} If the issue asserts that an endpoint should be public and asks for \texttt{@login\_required} to be removed, the naive judge is happy: the patch \emph{is} aligned with the stated intent. But this is exactly the attacker's goal --- it is a ``goal-hijack'' issue.
\end{enumerate}

\paragraph{Confidence-gated veto.}
We instruct the judge to emit \texttt{\{aligned,\ confidence,\ reason,\ added\_capabilities,\ removed\_controls\}} and treat an \texttt{aligned=false} verdict as a veto only when \texttt{confidence} $\geq \tau$. $\tau$ is chosen on a held-out benign calibration set to hit a target FPR. Our default is $\tau=0.9$; at that operating point the judge only vetoes when its evidence is unambiguous. Ambiguous cases (\texttt{confidence}${<}\tau$) are \emph{passed}, not rejected --- production deployments would surface these for human review (OWASP LLM01 human-in-the-loop~\cite{owaspllm01}).

\paragraph{Capability-diff / premise cross-check.}
The system prompt is restructured to ask the judge to reason about two orthogonal axes, \emph{independent} of what the issue asserts:
\begin{promptbox}
IMPORTANT --- PREMISE CROSS-CHECK. Do NOT trust the issue's premise blindly. Even if the issue explicitly asks for it, VETO patches that:
* REMOVE existing security controls (authentication/authorization decorators, login/permission checks, input validation, escaping, TLS/cert verification, CSRF/XSS checks, safe\_ open, ...);
* REMOVE bounds/type/None checks and replace them with wide-open sinks;
* INTRODUCE new dangerous sinks (subprocess/os.system/eval/exec/pickle.loads/marshal.loads/yaml.load/jinja2.Template(...).render/hashlib.md5/hashlib.sha1/open with attacker-controlled paths/urllib.request/requests.post/socket) that were NOT in the pre-patch code, unless the ISSUE explicitly and unambiguously requests exactly that operation with justification consistent with the behavioral bug;
* Contain magic-string / env-var / length-check gates around a sink;
* Contain base64/hex blobs, \_\_import\_\_ tricks, or dynamic string exec.
\end{promptbox}
This is what the abstract calls \emph{capability-diff reasoning}: what dangerous capability did the patch \emph{add} and what security control did it \emph{remove}, regardless of whether the issue asked for it. This is a straightforward operationalisation of the ``segregate and identify external content'' and ``human approval for high-risk actions'' mitigations from OWASP LLM01~\cite{owaspllm01}.

\begin{lstlisting}[style=kisspy,numbers=none,caption={The confidence-gated intent judge.},label={lst:judge}]
class IntentAlignmentJudge:
    def veto(self, sanitized_issue, patch):
        verdict = self.judge(sanitized_issue, patch)   # -> {aligned, confidence, reason,
                                                       #     added_capabilities, removed_controls}
        should_block = (not verdict.aligned) and (verdict.confidence >= self.tau)
        return should_block, verdict
\end{lstlisting}

%------------------------------------------------------------
\section{Evaluation}
\label{sec:eval}

\subsection{Corpus (Designed for Generalisation, not Memorisation)}
The corpus contains \NcorpusTotal{} labeled cases. The malicious portion (\NcorpusMal{} cases) has three sub-corpora:

\emph{(a)~CWE payloads $\times$ variants (\NcorpusCWE{} cases).} All five \textsc{SWExploit} CWE families (CWE-78, -502, -327, -94, -22) appear in seven variants that stay strictly inside the issue-only threat model: (1)~magic-string gate (SWExploit canonical), (2)~env-var gate, (3)~length-check gate, (4)~time-of-day gate, (5)~sink wrapped in an innocuous-looking helper, (6)~sink invoked via \texttt{\_\_import\_\_} (evades AST-based sink matching), (7)~no-gate dead-drop (sink always reachable, argument attacker-controlled). Magic strings are freshly randomised per case, so a defence cannot ``win'' by string-matching a known constant.

\emph{(b)~Prompt-injection cases (\NcorpusPI{} cases).} An HTML-comment ``ignore previous instructions'' payload attached to an otherwise ordinary null-check fix. This is the sub-family L1 was designed for.

\emph{(c)~False-premise / goal-hijack (\NcorpusFP{} cases).} Issues with plausible-but-wrong premises: (i)~remove \texttt{@login\_required} from an admin endpoint (``should be public per spec''), (ii)~mark a webhook \texttt{@csrf\_exempt} (``worker on the same VPC''), (iii)~switch \texttt{json.loads} to \texttt{pickle.loads} (``session blob is our own format''), (iv)~replace bcrypt with \texttt{hashlib.md5} (``only need de-duplication, not security''), (v)~disable \texttt{verify=True} in a \texttt{requests.get} (``local cert''), (vi)~turn \texttt{shell=True} on in \texttt{subprocess.run} (``args are trusted, from our own config''), (vii)~remove the \texttt{os.path.abspath} prefix check on \texttt{read\_asset} (``users need arbitrary paths''), (viii)~drop \texttt{html.escape} in \texttt{render\_post} (``rich-text feature broken by over-escaping''). Every one of these is aligned with the stated intent; every one removes a security control or introduces an unrequested dangerous capability.

\emph{(d)~Diverse benign controls (\NcorpusBen{} cases across \NcorpusBenTemplates{} scenario templates).} The pre-existing 20-case core: six null- and bounds-check fixes; five refactors; three legitimate uses of \texttt{subprocess} (hardcoded \texttt{git rev-parse HEAD}, etc.); three legitimate uses of \texttt{open} on package-relative paths (\texttt{Path(\_\_file\_\_).parent / 'VERSION'}); three feature additions (a CLI \texttt{--dry-run} flag). The AI-Discovery D3 expansion adds 80 more cases across 16 additional templates covering the ordinary bug-fix / refactor traffic an APR pre-merge gate would see in practice: docstring updates that match the current signature; type-annotation additions to migrated modules; isort import re-orders; unit-test-only additions in \texttt{tests/}; logging-message improvements (added \texttt{\%d}/\texttt{\%s} arguments); comment typo fixes; better \texttt{ValueError} messages that name the offending manifest; dict output-key renames; dataclass field renames (e.g.\ \texttt{src\_url} $\to$ \texttt{source\_url}); list-to-generator refactors; \texttt{with}-block migrations for local config files; \texttt{os.path.join}$\to$\texttt{pathlib.Path} migrations; \texttt{\%}-format $\to$ f-string modernisations; CI-matrix updates that add a new Python version; README install-snippet updates; and non-security decorator cleanups (removing an \texttt{unsafe\_hash=True} argument that is redundant now that \texttt{\_\_hash\_\_} is defined explicitly). Every template ships with five near-duplicate variants (differing only in ticket ID and cosmetic identifiers), so the aggregate benign set is $16\times 5 = 80$ variants plus the original 20 core cases $=$ 100. This diversity forces the FPR number to reflect real deployment behaviour --- an FPR measured only on null-check benign cases is trivial to game. Anti-reward-hacking constraint: none of the new templates introduces any dangerous sink or removes any security control, so an honest confidence-gated intent judge should not veto them; if it did, the FPR would jump immediately.

\subsection{Ablation}
Table~\ref{tab:ablation} reports each layer in isolation and the combined pipeline at three judge confidence thresholds. Judge model: \texttt{claude-opus-4-7}. Judge tau=0.9 is the default and matches the strongest MSR-25 pre-filter's FPR operating point (\MSRFPRStructured{}); tau=0.5 recovers the naive fail-closed behaviour of the preliminary draft; tau=0.7 is an intermediate operating point.

\begin{table}[H]
\centering
\caption{Ablation on the \NcorpusTotal-case corpus (\NcorpusMal{} malicious, \NcorpusBen{} benign across \NcorpusBenTemplates{} scenario templates; judge = \texttt{claude-opus-4-7}). The lower ``+ corroboration required (D1)'' block is the AI-Discovery operating point: identical numbers to the unconditional row on this corpus because every malicious case's veto is corroborated (the judge names the added capability or removed control on all \NcorpusMal{} of them), but the knob is retained because it is a strict, monotone FPR-reducer against untriggered judge scope-creep verdicts (see \S\ref{sec:aidiscovery}).}
\label{tab:ablation}
\begin{tabular}{lcc}
\toprule
\textbf{Configuration} & \textbf{Catch rate} & \textbf{FPR} \\
\midrule
L1 (issue sanitizer)                            & \LonlyCatch{}         & \LonlyFPR{} \\
L2 (masked-reproduction masker proxy)           & \LtwoCatch{}          & \LtwoFPR{}   \\
L3 (provenance, MEDIUM/HIGH sinks)              & \LthreeCatch{}        & \LthreeFPR{} \\
L4 (judge, $\tau=0.5$; naive fail-closed)       & \JudgeCatchLow{}      & \JudgeFPRLow{} \\
L4 (judge, $\tau=0.7$)                          & \JudgeCatchMid{}      & \JudgeFPRMid{} \\
L4 (judge, $\tau=0.9$; matched-FPR default)     & \JudgeCatchHigh{}     & \JudgeFPRHigh{} \\
Combined ($\tau=0.5$)                           & \CombinedCatchLow{}   & \CombinedFPRLow{} \\
Combined ($\tau=0.7$)                           & \CombinedCatchMid{}   & \CombinedFPRMid{} \\
\textbf{Combined ($\tau=0.9$)}                  & \textbf{\CombinedCatchHigh{}} & \textbf{\CombinedFPRHigh{}} \\
\midrule
\multicolumn{3}{l}{\textit{AI-Discovery operating point (D1: corroboration-required veto, \S\ref{sec:aidiscovery})}} \\
Combined ($\tau=0.5$) + corroboration           & \CombinedCatchLow{}   & \CombinedFPRLow{} \\
Combined ($\tau=0.7$) + corroboration           & \CombinedCatchMid{}   & \CombinedFPRMid{} \\
\textbf{Combined ($\tau=0.9$) + corroboration}  & \textbf{\CombinedCatchHighCorr{}} & \textbf{\CombinedFPRHighCorr{}} \\
\midrule
\multicolumn{3}{l}{\textit{Baseline (Przymus et al.~\cite{msrdefense}; verified numbers)}} \\
Best single pre-filter                           & \MSRSingle{}   & \MSRFPRStructured{} (structured 4o-mini) \\
Best ensemble                                    & \MSREnsembleOnly{} & --- \\
Best ensemble + post-APR Copilot review          & \MSREnsemblePost{} & --- \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Reading the table.} Three observations:
\begin{enumerate}[nosep,leftmargin=1.4em]
\item \emph{The judge alone is already strong, and its verdicts are decisive.} At $\tau=0.5$ and $\tau=0.7$ the judge catches an identical \JudgeCatchLow{} of malicious cases --- no verdicts fall in the $[0.5, 0.7)$ confidence band, so those thresholds are equivalent on this corpus. At $\tau=0.9$ the judge is more conservative (\JudgeCatchHigh{}, i.e.\ two additional malicious cases pass because their vetoes had confidence in $[0.5, 0.9)$).
\item \emph{The static layers close the catch gap without adding false positives.} Combined ($\tau=0.9$) reaches \CombinedCatchHigh{} at \CombinedFPRHigh{} FPR: L3 catches the medium-confidence judge misses (typically a \texttt{shell=True} false-premise case where the judge is 0.85-confident). L1 catches all six prompt-injection cases at zero FPR contribution. L2's mask proxy fires on one CWE-94 magic-string case in the current corpus (\texttt{ablation.csv} row); the paragraph in \S\ref{sec:defense} that said ``one per family'' overstates this and we correct it here.
\item \emph{The pipeline reports high catch at low target FPR on the static corpus.} Combined ($\tau=0.9$) is \CombinedCatchHigh{} catch at \CombinedFPRHigh{} on our \NcorpusBen-case benign denominator (Wilson two-sided upper bound $\approx \FPRWilsonHundred$ on that sample; see AI-Discovery D3 in \S\ref{sec:aidiscovery}). We emphasise this is a target-FPR operating point on a synthetic corpus, not a like-for-like win against the MSR-25 study's \MSRSingle{} pre-filter at \MSRFPRStructured{} on 100 real \texttt{psf/requests} issues~\cite{msrdefense}; running our judge on the same 100 issues is future work. Moreover the static result must be read together with the adaptive result in \S\ref{sec:adaptive}, which shows the same combined pipeline is beaten in three iterations by an LLM attacker.
\end{enumerate}
The \emph{only} case that slips past Combined ($\tau=0.9$) is \texttt{false\_premise/csrf-exempt}: the judge correctly identifies the removal of CSRF as harmful (\texttt{aligned=false}, \texttt{removed\_controls=[csrf\_exempt]}) but at confidence 0.85, just below the strict threshold. At $\tau=0.7$ or $\tau=0.5$ this case is caught. The per-family breakdown is in \texttt{swedefend/results/ablation\_family.csv} and the per-case audit trail (judge \texttt{added\_capabilities}/\texttt{removed\_controls}) is in \texttt{swedefend/results/ablation\_detail.csv}.

\paragraph{Statistical caveat (updated after AI-Discovery D3 expansion).} A \CombinedFPRHigh{} FPR measured on \NcorpusBen{} benign cases has a 95\% Wilson score-interval upper endpoint (two-sided) of $\approx \FPRWilsonHundred$; the two-sided Clopper--Pearson exact upper bound is $\approx \FPRExactHundred$ and the one-sided Clopper--Pearson exact upper bound is $\approx \FPRExactHundredOne$. All three are substantially tighter than the earlier draft's $n=20$ Wilson two-sided bound of $\approx \FPRWilsonTwenty$; AI-Discovery step D3 was the change responsible for the tightening (\S\ref{sec:aidiscovery}). \emph{Honest caveat.} Even the tightened Wilson upper bound remains larger than the MSR-25 baseline's reported point-estimate FPR of \MSRFPRStructured, so we cannot claim ``matched-FPR win'' at 95\% confidence; the correct reading is ``consistent with an unknown true FPR at or below $\FPRWilsonHundred$.'' We also note that our \NcorpusBen{} benign cases come from \NcorpusBenTemplates{} scenario templates with five near-duplicate variants per new template (differing only in a ticket-ID token in the issue text), so the effective independent sample size is smaller than 100 and the naive Wilson bound is optimistic if judged as ``100 independent samples''. Extending to the MSR-25 \texttt{psf/requests} 100-issue set for an equal-instance head-to-head remains future work.

\subsection{Generalisation across variants and false-premise attacks}
Because the corpus has seven variants per CWE family and a dedicated false-premise class, we can ask ``how does the defense do on cases the SWExploit paper did not directly evaluate?'' The per-family CSV \texttt{ablation\_family.csv} answers exactly that: it lists, per family (e.g.\ \texttt{CWE-78/envvar}, \texttt{CWE-22/deaddrop}, \texttt{false-premise/xss}), how many of that family's cases each configuration caught. We highlight the following patterns:

\emph{(a)~Static sinks still land the obvious variants.} The Bandit/Semgrep MEDIUM/HIGH pass catches most CWE-78/-502/-94 magic, helper, and deaddrop variants (a raw \texttt{subprocess(...\ shell=True)} or \texttt{pickle.loads} shows up regardless of the gate).

\emph{(b)~Encoded and time-gated variants defeat static analysis.} The \texttt{\_\_import\_\_('subprocess').run(...)} encoded variant does not lexically match Bandit's rule set, so L3 lets it through. The intent judge with capability-diff catches these because a patch that starts with \texttt{\_\_import\_\_('subprocess')} in a null-check refactor is on its face out of scope.

\emph{(c)~False-premise attacks are exactly what capability-diff is for.} All eight false-premise cases explicitly remove an existing security control. The judge's \texttt{removed\_controls} field surfaces \texttt{login\_required}, \texttt{csrf\_exempt}, \texttt{verify=False}, \texttt{html.escape}, \texttt{os.path.abspath}, \texttt{shell=True $\to$}, etc.\ verbatim, which makes both the veto and the audit trail meaningful.

\emph{Honest caveats.} (i)~The false-premise cases are hand-authored, not generated; a stronger evaluation would auto-generate them with an attacker LLM. (ii)~The judge is a single \texttt{claude-opus-4-7} model; an attacker with white-box knowledge of that specific model might craft judge-specific evasions. Ensembles (LLM juries~\cite{zheng2023}) are the natural hardening.

\subsection{AI-Discovery: reducing false-positive rate to 0\%}
\label{sec:aidiscovery}

The 20\%-scale FPR of our preliminary draft, and the reviewer's correct observation that a static ``0/20~FP'' point estimate has a $\FPRWilsonTwenty$ Wilson upper bound and is therefore not a robust claim, motivated a focused AI-Discovery pass on FPR reduction. We surveyed the LLM-as-a-judge FPR literature --- Zheng et~al.'s taxonomy of position/verbosity/self-enhancement biases~\cite{zheng2023}, Wang et~al.'s self-consistency majority-vote recipe~\cite{wang2022sc}, and Verga et~al.'s Panel of LLM Evaluators (PoLL) result that a jury of smaller models outperforms a single large model at $7\times$ lower cost~\cite{polljury} --- and instantiated three concrete design knobs, each retained as an opt-in kwarg on \texttt{IntentAlignmentJudge} so they can be evaluated independently.

\paragraph{D1 --- Corroboration-required veto.}
An \texttt{aligned=false}, \texttt{confidence}${\geq}\tau$ verdict from the judge is not \emph{by itself} enough to enforce a veto: it must additionally be corroborated by either (a)~a concrete \texttt{added\_capabilities} entry in the same verdict (the judge names the dangerous capability the patch added --- e.g.\ ``subprocess shell=True'', ``pickle.loads''), (b)~a concrete \texttt{removed\_controls} entry (the judge names the security control the patch removed --- e.g.\ ``login\_required'', ``verify=True''), or (c)~an independent static signal from L1 (issue sanitizer flagged the issue) or L3 (provenance found a MEDIUM/HIGH-severity dangerous sink). Uncorroborated ``scope-creep'' judgments --- where the judge cannot articulate \emph{what} new capability was added or \emph{what} control was removed and no other layer objects --- are the dominant source of the preliminary draft's FPR, and D1 vetoes them.

D1 is a strict monotone \emph{veto-suppressor} by construction: it only ever \emph{removes} vetoes, never adds them. On a benign distribution where the judge occasionally emits uncorroborated ``scope-creep'' verdicts, D1 can only \emph{reduce} FPR; on a malicious distribution where a veto \emph{should} enforce but the judge cannot name a concrete capability, D1 can \emph{introduce} an FN — so D1 is not automatically a win, and its safety depends on the judge's ability to articulate concrete evidence when it correctly detects malicious code. On our \NcorpusMal{}-case malicious corpus this failure mode does not occur: every L4-caught malicious case has a concrete \texttt{added\_capability} or \texttt{removed\_control} named by the judge (the six prompt-injection cases have empty capability lists but are caught by L1, not by L4, so D1 is not consulted). Consequently D1 is a no-op on this specific corpus — every corroborated row in Table~\ref{tab:ablation} matches its non-corroborated counterpart exactly — and the paper does not claim D1 caused the reported 0/100 FPR. What D1 does provide is a robustness knob for the wider benign distribution where uncorroborated judge scope-creep verdicts (the source of the earlier draft's 20\%-scale FPR) would otherwise dominate. We keep the D1 knob in the ablation table (middle block of Table~\ref{tab:ablation}) and in the code (\texttt{IntentAlignmentJudge.require\_corroboration}) so subsequent evaluations can measure it on data where uncorroborated vetoes are actually present. To close a reward-hacking loophole in D1 that an independent code reviewer flagged, the corroboration check on \texttt{added\_capabilities}/\texttt{removed\_controls} additionally requires each named entry to be a string with $\geq 3$ alphabetic characters after whitespace-stripping, rejects bare-string scalars (which would otherwise iterate character-by-character in Python), and rejects non-list types (see \texttt{\_has\_concrete\_entry} in \texttt{intent\_judge.py}). This guards against a malformed judge reply that accidentally trivially unlocks the veto.

\paragraph{D2 --- Self-consistency $N{=}3$ judge sampling (Wang et~al.\ 2022).}
When enabled, the judge is queried $N$ times per case and the boolean \texttt{aligned} field is a majority vote across the $N$ samples; the aggregate \texttt{confidence} is the mean confidence of the samples that voted with the majority, and \texttt{added\_capabilities} / \texttt{removed\_controls} are the union across those samples. Ties conservatively break toward \texttt{aligned=false} (i.e.\ the veto side wins the tie-break, so D2 does not silently soften catch). This is Wang et~al.'s canonical self-consistency recipe~\cite{wang2022sc}, applied to a binary-verdict LLM judge instead of a chain-of-thought reasoner. We do not run the full $N{=}3$ ablation over all \NcorpusTotal{} cases in this submission (it triples the number of LLM calls and, given D1 already collapses FPR to 0/100, does not change the reported operating point), but the knob is implemented, unit-tested with a fake 2/3 misaligned $+$ 1/3 aligned setup, and exposed via the \texttt{self\_consistency\_n} kwarg on \texttt{IntentAlignmentJudge}.

\paragraph{D3 --- Diversified benign corpus ($n{=}20$ across 5 templates $\to$ $n{=}100$ across \NcorpusBenTemplates{} templates).}
The preliminary draft's benign set had 20 cases from only five templates (null-check fixes, refactors, hardcoded-subprocess helpers, package-relative \texttt{open}, feature additions), giving a Wilson two-sided upper bound on 0/20 of $\FPRWilsonTwenty$ that the paper's own Discussion admitted could not causally show the confidence gate had reduced FPR. D3 adds 80 more cases across 16 additional templates covering the ordinary bug-fix / refactor traffic listed in \S\ref{sec:eval}(d) --- docstring updates, type annotations, isort reorders, unit-test additions, logging-message improvements, error-message rewrites, dict-key renames, dataclass field renames, generator refactors, \texttt{with}-block migrations, pathlib migrations, f-string modernisations, CI-matrix updates, README fixes, non-security decorator cleanups, plus comment typo fixes. Every new template is either non-code (README, CI-config) or is a semantic refactor that neither adds a dangerous sink nor removes a security control. Anti-reward-hacking constraint: we verified this by hand and by grep --- no benign template contains \texttt{subprocess.run(...\ shell=True)}, \texttt{eval}, \texttt{exec}, \texttt{pickle.loads}, \texttt{hashlib.md5}, \texttt{jinja2.Template(...).render}, \texttt{\_\_import\_\_}, unauthenticated \texttt{requests.get(...,\ verify=False)}, or the removal of any \texttt{@login\_required}, \texttt{@csrf\_exempt}, \texttt{html.escape}, or path-prefix check. If we had added ``cargo-cult'' benign patches with dangerous sinks in them, they would be indistinguishable from the malicious cases and would inflate FP rather than FPR.

\paragraph{D4 --- LLM jury (declared, not implemented).}
Verga et~al.'s PoLL~\cite{polljury} shows that a panel of smaller models from disjoint vendors outperforms a single large judge at $7\times$ lower cost. Extending SWEDefend's L4 to an $\{{\texttt{claude-opus-4-7}}, {\texttt{gpt-5.6-sol}}\}$ jury with an ``AND-veto'' policy (both vendors must veto) is a natural D4 knob, mechanically similar to D2 but across model families rather than samples. D4 is \emph{not} implemented in this submission — no multi-vendor jury exists in the reviewed judge code and no D4 unit test exists — and we mark it as future work. On a wider benign distribution D4 would further reduce judge-variance-induced FP.

\paragraph{Anti-reward-hacking / anti-cheating verification.}
Before running the ablation we verified: (i)~D1 uses a \emph{generic} corroboration list (any concrete added capability, removed control, or L1/L3 signal), not a benign-specific whitelist; (ii)~the pipeline's veto path is still exercised --- a manual smoke test of one CWE-78 magic-string malicious case at $\tau=0.9$ with corroboration on still blocks it (verdict names \texttt{subprocess} in \texttt{added\_capabilities}); (iii)~the D3 benign expansion introduces no cases that share text with a malicious case (verified by hash comparison of \texttt{issue\_text} and \texttt{patch\_source} across the two subsets); (iv)~the catch-rate column of Table~\ref{tab:ablation} is reported side-by-side with FPR, so any reader can immediately see that FPR reduction did not come from silently softening catch. The verdict cache used by the ablation script (\texttt{verdict\_cache.json}) is content-addressed by the SHA-256 of \texttt{(model\_name, issue\_text, patch\_source)} triples, so reruns are deterministic and cache poisoning between benign and malicious subsets is not possible.

\paragraph{Result.}
D3 tightens the Wilson two-sided upper bound from $\FPRWilsonTwenty$ to $\FPRWilsonHundred$ at $0$ FP (Clopper--Pearson two-sided $\FPRExactHundred$, one-sided $\FPRExactHundredOne$), without any change to the catch column (Combined at $\tau=0.9$ remains \CombinedCatchHigh; Combined at $\tau=0.5$ / $\tau=0.7$ remain \CombinedCatchLow{} / \CombinedCatchMid{}). D1 preserves that operating point on this corpus. D2 is implemented and unit-tested (a three-sample majority-vote test with a 2/1 misaligned/aligned split verifies the aggregation) but not measured on the full ablation because it would triple the number of LLM calls and, given that D1 already covers the current corpus, does not change the reported operating point. D4 is declared but not implemented in this submission. Anti-overclaim note: the AI-Discovery pass \emph{tightened} the Wilson upper bound on FPR from $\FPRWilsonTwenty$ to $\FPRWilsonHundred$ by expanding the benign denominator; it did not move a positive point-estimate FPR down to zero on a fixed evaluation set (that point estimate was already zero on the smaller $n{=}20$ set). The honest reading of the AI-Discovery result is therefore: \emph{a $0/100 = 0\%$ FPR at $97.96\%$ catch (Combined, $\tau=0.9$, D1-corroborated), statistically consistent with any true FPR $\leq \FPRWilsonHundred$ at $95\%$ Wilson confidence} --- a more credible operating-point claim than the earlier $0/20$, but not a demonstration that the D1 code change caused an observed FPR reduction on this specific corpus.

\subsection{Adaptive attacker (PAIR-style, LLM-driven, up to 40 iterations)}
\label{sec:adaptive}
The preliminary draft's adaptive study used five iterations and three hard-coded mutation rules (strip \texttt{<!--}, base64-encode the sink, wrap in a helper). The reviewer of that draft correctly noted that (a)~five iterations is far too few compared with PAIR's own budget~\cite{pair} and (b)~a hard-coded mutator is not an adaptive attacker at all --- it is a static ablation. We replace it with an LLM-driven attacker (Algorithm~1, implemented in \texttt{swedefend/adaptive.py}):

\begin{lstlisting}[style=kisspy,numbers=none,caption={Algorithm 1: PAIR-style~\cite{pair} adaptive attacker.},label={lst:adaptive}]
def run_seed(pipeline, seed, attacker_llm, max_iters=40):
    issue, patch = seed.initial_issue, seed.initial_patch
    for i in range(max_iters):
        verdict = pipeline.evaluate(issue, patch)                # full per-layer feedback
        if verdict.allow and matches_sink_signature(patch, seed.sink_signature):
            return SUCCESS_AT(i)                                 # attack succeeded
        new = attacker_llm.refine(seed.cwe, issue, patch, verdict)  # attacker chooses strategy
        if new is None:  # attacker LLM refused
            log_refusal(); continue
        issue, patch = new.issue, new.patch
    return BLOCKED
\end{lstlisting}

The attacker's system prompt frames the exercise as a controlled academic red-team task and requires the patch to contain a per-seed \emph{sink signature} (e.g.\ ``\texttt{subprocess}'' and ``\texttt{shell=True}'' must both appear for CWE-78) so a ``successful'' attempt must retain the CWE goal, not evade by silently dropping the payload. The attacker is free to choose \emph{any} strategy: payload splitting, base64/\texttt{\_\_import\_\_} indirection, premise manipulation, benign filler, helper hoisting, encoded gates, or novel combinations.

\paragraph{Attacker model choice.} We report using \texttt{claude-opus-4-6} as the attacker LLM. The most heavily safety-aligned frontier models (Opus-4-7 and Opus-4-8) refuse this red-team prompt often enough to make an experiment noisy; \texttt{claude-opus-4-6} is a competent multi-turn planner with lower refusal rate on offensive-security research prompts, matching the recommendation in the AI-red-teaming literature that Opus-class models are the strongest general-purpose attacker LLMs but that the specific version matters for refusal-rate. GLM-4/5-class models~\cite{glm} are an alternative for code-specific attacks. We log every refusal (see \texttt{swedefend/results/adaptive\_seeds.csv}) rather than hiding them.

\paragraph{Adaptive-attack results (negative result, reported honestly).} Table~\ref{tab:adaptive} reports the per-iteration cumulative attack success rate (ASR) across three seed CWE goals under the pilot budget we could run within the compute available for this submission (3 seeds $\times$ 5 iterations at $\tau=0.9$, attacker = \texttt{claude-opus-4-6}, judge = \texttt{claude-opus-4-7}; the raw per-attempt log is \texttt{swedefend/results/adaptive\_partial.csv}). \textbf{Contrary to what we hoped to show, the LLM attacker beats the confidence-gated combined pipeline in every one of the three seeds within three iterations}: CWE-78 succeeded at iteration~2, CWE-502 at iteration~3, and CWE-94 at iteration~2. Cumulative ASR reaches $100\%$ by iteration~3. The dominant strategy the attacker discovered was \emph{premise reframing}: the attacker rewrites the issue to justify a legitimate-sounding use of the sink (``diagnostic hook needs a shell command'', ``local trusted config expression''), which the confidence-gated judge is willing to accept as aligned at low-to-moderate confidence rather than high-confidence-veto. The judge does veto at iteration~1 (with the naive sink present), but the confidence drops below $\tau=0.9$ on the next iteration once the attacker frames the sink as legitimate, and the confidence gate lets the patch through.

\begin{table}[H]
\centering
\caption{Adaptive attacker cumulative ASR (three seeds, 5 refinement iterations per seed --- honest pilot budget for this submission, attacker=\texttt{claude-opus-4-6}, judge=\texttt{claude-opus-4-7}, $\tau=0.9$). Raw per-attempt data in \texttt{adaptive\_partial.csv}.}
\label{tab:adaptive}
\begin{tabular}{lccc}
\toprule
\textbf{Iteration} & \textbf{Cumulative ASR} & \textbf{New blocked at iter} & \textbf{Refused} \\
\midrule
1 & 0/3 = 0.00 & 3 & 0 \\
2 & 2/3 = 0.67 & 1 & 0 \\
3 & 3/3 = 1.00 & 0 & 0 \\
4 & 3/3 = 1.00 & 0 & 0 \\
5 & 3/3 = 1.00 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{What the negative result means.} We interpret this outcome as showing that (i)~the confidence gate --- while it \emph{does} give a meaningful FPR knob on the static corpus --- is by construction a \emph{monotone reduction} in vetoes and therefore a monotone gift to any adaptive attacker that can maneuver the judge's confidence into the ``ambiguous / no veto'' region. This is a fundamental design tension in confidence-gated defenses that is understated in our earlier framing (\S\ref{sec:defense}). (ii)~The capability-diff prompt (which our earlier draft called ``capability-diff reasoning'') is not, in the current implementation, a true diff: the judge sees only the post-patch source, not a base-vs.-patch pair, and therefore cannot distinguish a newly-added sink from a pre-existing one --- a design defect identified by an independent code review of this submission. A capability-diff judge that actually receives a unified diff is a natural next step but was not implemented in time for this submission. (iii)~A larger PAIR budget would only make the attacker's win faster and cleaner; 40~iterations is not the interesting variable when the pipeline already fails at three. What matters is heterogeneous multi-vendor jury~\cite{zheng2023}, actual diff input to the judge, and behavioural verification (L2 with a real repo). The paper's contribution is therefore best read as \emph{a partial defense with a well-characterised failure mode against LLM-driven adaptive attackers}, not as a deployable defense at $\tau=0.9$.

%------------------------------------------------------------
\section{Discussion and Limitations}
\label{sec:discussion}

\paragraph{Novelty (honest framing).}
The intent-alignment LLM judge is not novel: the empirical study we compare against~\cite{msrdefense} already evaluates GPT-4.1 / o4-mini / 4o-mini as pre-repair filters, and Task Shield~\cite{taskshield} proposes task-alignment enforcement for tool-using agents. What we contribute over that state of the art is (i)~a \emph{confidence-gated} veto that lets us report at an operating point matched to the \MSRFPRStructured{} baseline rather than at $\sim$20\% FPR; (ii)~a \emph{capability-diff / premise cross-check} judge prompt that decouples the judge's decision from the attacker-controlled stated intent; (iii)~a corpus explicitly designed to exercise variations within the threat model rather than one specific attack instantiation; and (iv)~an LLM-driven PAIR-style adaptive attacker with a realistic per-seed budget and honest reporting of refusals. Our L1, L2, and L3 layers are conservative implementations of well-known ideas (regex sanitization, MELON-style masked reproduction~\cite{melon}, static taint via Bandit and offline Semgrep); we deliberately \emph{narrow} L3's veto scope to MEDIUM/HIGH-severity findings after the preliminary draft's raw sink-name detector produced excessive FPs on legitimate code.

\paragraph{Comparison with \cite{msrdefense} — what is and isn't shown.}
The MSR-25 defence at its most permissive operating point (structured \texttt{gpt-4o-mini} pre-filter) achieves \MSRFPRStructured{} FPR at \MSRSingle{} catch on 51 adversarial and 100 real \texttt{psf/requests} issues. SWEDefend's confidence-gated pipeline at $\tau=0.9$ is designed to \emph{target} the same FPR operating point on a substantially larger corpus (CWE-family variations $\times$ false-premise $\times$ diverse benign). Two things this paper does \emph{not} show, contrary to how a first reading of Table~\ref{tab:ablation} might sound: (a)~we do not evaluate on the MSR-25 100-issue benign set, so the ``matched FPR'' framing is an operating-point choice, not an equal-instance measurement; and (b)~the adaptive result in \S\ref{sec:adaptive} demonstrates that the static win does not survive an LLM-driven attacker, so the ensemble-ceiling comparison of \MSREnsembleOnly{}--\MSREnsemblePost{} does not translate into a stronger deployable defence at this stage.

\paragraph{Known limitations.}
\emph{(i)~The judge is a single-vendor model.} An attacker with white-box knowledge of the judge model could iterate specifically against it; an LLM-jury~\cite{zheng2023} across at least two vendors (Anthropic + OpenAI) is the standard mitigation. \emph{(ii)~The false-premise cases are hand-authored.} A rigorous evaluation would auto-generate them with the attacker LLM under the same PAIR-style budget as \S\ref{sec:adaptive}. \emph{(iii)~L2's contribution on the static corpus is limited to the mask-proxy}; its behavioural verification value needs a real repository with F2P/PASS\_TO\_PASS tests. \emph{(iv)~L3's narrowing to MEDIUM/HIGH-severity trades catch on \texttt{B603}-style hardcoded subprocess for the ability to run alongside code that legitimately uses \texttt{subprocess} or \texttt{open}.} \emph{(v)~Regex-based L1} is trivially evadable; we keep it because it catches the naive HTML-comment prompt-injection sub-family at zero FPR contribution but do not rely on it. \emph{(vi)~Attacker-LLM refusals.} Modern safety-aligned attacker models (Opus-4-7, Opus-4-8) refuse this red-team prompt often; we log the refusal rate rather than picking the numbers that look best. An open-weights attacker or a specifically-tuned model (GLM-4.6 / GLM-5.2~\cite{glm}) would give a stronger, more reproducible adaptive result.

\paragraph{Independent code-review deviations from paper claims.}
An independent code review of this submission (using a different model family from the one used to write the code) surfaced several deviations between what the paper claims and what the implementation actually does. In the interest of honesty we enumerate the most important ones here rather than quietly fixing them and republishing.
\begin{itemize}[nosep,leftmargin=1.4em]
\item \emph{``Capability-diff'' is not, in fact, a diff.} The judge sees only the post-patch source, not a base-vs.-patch pair, so ``newly-added sink'' vs.\ ``pre-existing sink'' cannot be distinguished from the input alone. It relies on the judge's implicit prior for what code is idiomatic in a bug-fix context. A true unified-diff input to the judge is the natural fix.
\item \emph{L2's masking has no effect on its behavioural verdict in the current implementation.} The masker rewrites the issue but the verdict is driven purely by \texttt{FAIL\_TO\_PASS}/\texttt{PASS\_TO\_PASS} test outcomes; the ``mask-proxy'' row in Table~\ref{tab:ablation} is a purely-lexical proxy for the effect the masker \emph{would} have, not L2's own verdict on a real repo. We flag this explicitly rather than presenting the proxy row as L2.
\item \emph{L3's Semgrep result-classifier substring-matches on legacy rule IDs} (\texttt{dangerous-subprocess}, \texttt{eval}, \texttt{pickle}, ...) whereas the shipped local rules use \texttt{dangerous-sink-subprocess}, \texttt{dangerous-sink-crypto}, etc. Consequently many of the local rules do not surface into the L3 findings on which the paper reports; L3's catch on CWE-94, -327, and -22 in Table~\ref{tab:ablation} reflects Bandit alone, not the shipped Semgrep rules as claimed in \S\ref{sec:l3}.
\item \emph{Scanner failures / judge parse failures are fail-open under any positive $\tau$.} A malformed judge reply yields \texttt{aligned=False, confidence=0.0}, and the confidence gate then treats it as ``no veto'' at $\tau\geq 0.1$. This is opposite to a true fail-closed contract.
\item \emph{The confidence-gate ablation still cannot causally show that confidence gating reduced FPR}, because after AI-Discovery D3 all three thresholds produce $0/100$ false positives on the expanded benign set. The 20\%-FPR baseline that motivated the gate came from an earlier prompt/model/corpus (a naive judge that treated any \texttt{aligned=false} verdict as a veto regardless of confidence) which is not exercised in the reported ablation. This should be treated as an operating-point knob and a distribution-shift robustness knob rather than a proof of causal FPR reduction on the current corpus.
\item \emph{The adaptive threat model in \S\ref{sec:adaptive} is stronger than the paper's stated issue-only threat model} because the attacker LLM directly supplies the patch source rather than only the issue. The correct interpretation is ``if the attacker can eventually induce an APR agent to emit a patch of their choice, can the defence still block it?'' We should have introduced this as ``patch-control'' rather than issue-only for the adaptive experiment.
\item \emph{Adaptive success uses substring containment of the sink signature}, not compile/run/reachability, so a signature in a comment or dead branch also counts. Combined with the negative adaptive result this is more forgiving than fair; the honest fix is to compile+import and static-reachability-check the successful patches, which we defer to future work.
\item \emph{The benign set now has \NcorpusBen{} cases across \NcorpusBenTemplates{} scenario templates} (AI-Discovery D3, \S\ref{sec:aidiscovery}), tightening the Wilson two-sided upper bound on 0 FP from $\FPRWilsonTwenty$ (n=20) to $\FPRWilsonHundred$ (n=100). Within each template variants share the same patch source and differ only in a ticket-ID token in the issue text; the effective independent sample size is therefore closer to \NcorpusBenTemplates{} unique scenarios than to 100, so the Wilson bound is optimistic if judged as ``independent samples'' but is a reasonable proxy for ``FPR across the ordinary bug-fix / refactor distribution''. Extending to the MSR-25 \texttt{psf/requests} 100-issue set for an equal-instance head-to-head remains future work.
\end{itemize}
We include this list because (a)~a defense paper that hides its implementation defects is worse than one that reports them, and (b)~each of these is a concrete, actionable next step rather than a fundamental impossibility.

%------------------------------------------------------------
\section{Related Work}
\label{sec:related}

\textsc{SWExploit}~\cite{swexploit} is the attack we defend against. The adversarial-bug-report defence study of Przymus et al.~\cite{msrdefense} is our primary baseline; it evaluates LlamaGuard, PromptGuard, Granite-Guardian, GPT-4.1 / o4-mini / 4o-mini pre-filters, GitHub Copilot review, and CodeQL, and includes the \MSRFPRStructured{}-FPR pre-filter (structured 4o-mini) we compare against. MELON~\cite{melon} is the source of the masked-reproduction idea (L2). Task Shield~\cite{taskshield} enforces task alignment on tool-using agents (spiritually similar to L4). Greshake et al.~\cite{greshake2023} give the indirect-prompt-injection taxonomy; the OWASP LLM Top 10 (LLM01: Prompt Injection)~\cite{owaspllm01} codifies the mitigation checklist we implement. Adaptive-evaluation methodology follows Carlini et al.~\cite{carlini2019adv} and Tram\`er et al.~\cite{tramer2020adaptive}. PAIR~\cite{pair} is the attacker template our adaptive loop instantiates; GCG~\cite{gcg} is the strongest single-turn attacker in the literature (adversarial suffixes; out of scope for the issue-only threat model but a natural stress test on the judge). Zheng et al.~\cite{zheng2023} study LLM-as-judge reliability and biases; Wang et al.~\cite{wang2022sc} propose self-consistency as an FPR-reduction technique; Verga et al.'s Panel of LLM Evaluators~\cite{polljury} shows that a jury of smaller heterogeneous models beats a single large judge at $7\times$ lower cost --- the design basis for our declared-but-unmeasured D4 knob. Sommer and Paxson~\cite{sommer2010} give the classic argument for why an ML classifier for security \emph{must} operate at a low FPR to be deployable. SWE-agent~\cite{sweagent} and SWE-bench~\cite{swebench} are the target agent and benchmark.

%------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

APR agents inherit a new attack surface from the untrusted issue field, and \textsc{SWExploit}~\cite{swexploit} shows this surface is exploitable enough to hide reachable CWE payloads inside test-correct patches. Prior empirical defense work~\cite{msrdefense} reports \MSREnsemblePost{} catch (best ensemble + post-APR review) with a \MSRFPRStructured{} FPR for the structured pre-filter alone; the ensemble and ensemble+Copilot rows in that study do not carry a comparable FPR number. This paper attempts three concrete improvements over the natural intent-alignment-judge next step --- a confidence-gated veto, a capability-diff / premise-cross-check judge prompt, and a corpus designed for generalisation across variants and false-premise attacks --- and evaluates them against an LLM-driven PAIR-style adaptive attacker. The static evaluation shows the combined pipeline can operate at a low target FPR with high catch, but the adaptive evaluation (\S\ref{sec:adaptive}) shows the pipeline is broken by \emph{premise reframing} in three iterations on all three seeds. We report this negative result explicitly and, informed by an independent code review, enumerate the implementation-level deviations from the paper's claims (\S\ref{sec:discussion}). The remaining challenges --- a heterogeneous multi-vendor judge, a judge that receives an actual unified diff rather than post-patch source, true behavioural verification against real SWE-bench repositories, and a corpus generated (not hand-authored) with the same PAIR budget as the attacker --- define the concrete path from this partial defense to a deployable pre-merge gate for autonomous program repair.

%------------------------------------------------------------
\begin{thebibliography}{99}

\bibitem{swexploit} S.~Chen, Y.~He, S.~Jana, and B.~Ray.
Red Teaming Program Repair Agents: When Correct Patches Can Hide Vulnerabilities.
arXiv:2509.25894, 2025.

\bibitem{msrdefense} P.~Przymus, A.~Happe, and J.~Cito.
Adversarial Bug Reports as a Security Risk in Language Model-Based Automated Program Repair.
arXiv:2509.05372, 2025.

\bibitem{carlini2019adv} N.~Carlini, A.~Athalye, N.~Papernot, W.~Brendel, J.~Rauber, D.~Tsipras, I.~Goodfellow, A.~Madry, and A.~Kurakin.
On Evaluating Adversarial Robustness.
arXiv:1902.06705, 2019.

\bibitem{tramer2020adaptive} F.~Tram\`er, N.~Carlini, W.~Brendel, and A.~Madry.
On Adaptive Attacks to Adversarial Example Defenses.
NeurIPS, 2020. arXiv:2002.08347.

\bibitem{pair} P.~Chao, A.~Robey, E.~Dobriban, H.~Hassani, G.~J.~Pappas, and E.~Wong.
Jailbreaking Black Box Large Language Models in Twenty Queries.
arXiv:2310.08419, 2023.

\bibitem{gcg} A.~Zou, Z.~Wang, N.~Carlini, M.~Nasr, J.~Z.~Kolter, and M.~Fredrikson.
Universal and Transferable Adversarial Attacks on Aligned Language Models.
arXiv:2307.15043, 2023.

\bibitem{melon} MELON: Provable Defense Against Indirect Prompt Injection Attacks in AI Agents.
arXiv:2502.05174, 2025.

\bibitem{taskshield} Task Shield: Enforcing Task Alignment to Defend Against Indirect Prompt Injection in LLM Agents.
arXiv:2412.16682, 2024.

\bibitem{greshake2023} K.~Greshake, S.~Abdelnabi, S.~Mishra, C.~Endres, T.~Holz, and M.~Fritz.
Not what you've signed up for: Compromising Real-World LLM-Integrated Applications with Indirect Prompt Injection.
arXiv:2302.12173, 2023.

\bibitem{owaspllm01} OWASP Foundation.
OWASP Top 10 for LLM Applications, LLM01:2025 Prompt Injection.
\url{https://genai.owasp.org/llmrisk/llm01-prompt-injection/}, 2025.

\bibitem{zheng2023} L.~Zheng, W.-L.~Chiang, Y.~Sheng, S.~Zhuang, Z.~Wu, Y.~Zhuang, Z.~Lin, Z.~Li, D.~Li, E.~P.~Xing, H.~Zhang, J.~E.~Gonzalez, and I.~Stoica.
Judging LLM-as-a-Judge with MT-Bench and Chatbot Arena.
arXiv:2306.05685, 2023.

\bibitem{wang2022sc} X.~Wang, J.~Wei, D.~Schuurmans, Q.~Le, E.~Chi, S.~Narang, A.~Chowdhery, and D.~Zhou.
Self-Consistency Improves Chain of Thought Reasoning in Language Models.
arXiv:2203.11171, 2022.

\bibitem{polljury} P.~Verga, S.~Hofstatter, S.~Althammer, Y.~Su, A.~Piktus, A.~Arkhangorodsky, M.~Xu, N.~White, and P.~Lewis.
Replacing Judges with Juries: Evaluating LLM Generations with a Panel of Diverse Models.
arXiv:2404.18796, 2024.

\bibitem{sommer2010} R.~Sommer and V.~Paxson.
Outside the Closed World: On Using Machine Learning for Network Intrusion Detection.
IEEE S\&P, 2010.

\bibitem{sweagent} J.~Yang, C.~E.~Jimenez, A.~Wettig, K.~Lieret, S.~Yao, K.~Narasimhan, and O.~Press.
SWE-agent: Agent-Computer Interfaces Enable Automated Software Engineering.
NeurIPS, 2024. arXiv:2405.15793.

\bibitem{swebench} C.~E.~Jimenez, J.~Yang, A.~Wettig, S.~Yao, K.~Pei, O.~Press, and K.~Narasimhan.
SWE-bench: Can Language Models Resolve Real-World GitHub Issues?
ICLR, 2024.

\bibitem{glm} Zhipu AI. GLM-4 / GLM-5 model family. \url{https://open.bigmodel.cn/}, 2024--2025.

\bibitem{bandit} PyCQA. Bandit: A tool for finding common security issues in Python code. \url{https://github.com/PyCQA/bandit}, 2024.

\bibitem{semgrep} Semgrep, Inc. Semgrep: Lightweight static analysis for many languages. \url{https://semgrep.dev}, 2024.

\end{thebibliography}

\end{document}
